### 2016-10-13 Work_Flow_Plan.Rmd
First commit. Added Data folder, scripts folder, and workflow. Attempted to add file names to .gitignore. We will see if that actually works.

---
title: "Project Outline"
author: "Lacey Etzkorn"
date: "September 16, 2016"
output: 
      html_document:
            toc: TRUE
---

# Motivation
The goal of this project is to explore how people interact with online communities in regards to their own mental health. Specifically, we will collect data on Reddit, since this platform presents some unique opportunities for studying mental health:

* People post anonymously under a user name, which allows us to connect comments to common users and monitor user comments across time and subreddits.

* People often feel comfortable posting some (not all) personal thoughts and feelings on reddit, so we have access to some information people might not readily admit to health researchers.

# Possible Questions

* Understand post features of people who post on /r/depression. These features include: average time between posts. Average sentiment of posts. Difference in average sentiment of posts before and after suicide ideation. Proportion of posts in /r/depression or mental health-related subreddits.

* Predict suicide ideation using past user information. This past user information might include: Sentiment, Revealed Clinical Information, Relationship Status.

* Test whether features of comments on suicide ideation posts are associated with eventual outcomes. These outcomes might include: net increase in average sentiment, subsequent suicide ideation, etc...

# Data Collection Outline

We first scraped all posts and comments from /r/depression in the month of June 2016 using the package [insert package] with 5 minute intervals.
From now on, we will collectively refer to posts and comments as posts.
We then classified whether each post contained evidence of suicide ideation (SI). 
Details on the algorithm for classifying SI in posts is detailed in a subsequent section.
Once posts are classified, we identify the unique users who had any SI post, and then we download each of their post histories using our own program for querying the reddit API.
Since Reddit caps API requests to 1000 items, we are only able to grab the most recent 1000 posts and 1000 comments each for each user, so data on comments prior to 1000 posts and 1000 comments respectively are censored.

Once we have post histories for each user that had identified SI, we reclassify all of their comments with SI.

* Apply suicide ideation algorithm to this longitudional data

# Data

## June Data from /r/depression
We scraped 4,841 posts and 17,200 comments from the month of June 2016 representing 3,784 and 5,563 unique authors respectively.
The post data contained 385 identified admissions of suicide ideation from 364 unique authors.
The post data contained 162 identified admissions of suicide ideation from 147 unique authors.
Altogether, we identified 492 authors with admissions of suicide ideation in the month of June.

## Author Post History Data
After collecting post trajectories for each author with SI in June, we were unable to find any post or comment from just one author.

# What we are stuck on

#### Downloading user-specific post trajectories:

* We need to loop through a list of users we have previously identified as having suicide ideation and grab all of their posts.

* We don't know how to get to this json file via the API package PRAW. Is there another way to do this?

* We don't know the equivalent to clicking the "next" button.

# Methods

Entire reddit post trajectories were scraped for users who had a direct admission of suicide ideation in a post or comment in the month of June 2016.

Posts were classified as containing evidence of suicidal ideation if the post contained one of the phrases

### 2016-10-13 Scripts/1_Read_JSON_Files.R

@@ -1,0 +1,63 @@
+library(dplyr)
+
+### variable names
+comm.vars =
+      c("author", "created_utc", "likes", "score", "ups", "downs", 
+        "subreddit_id", "link_id", "id", "name", "parent_id",        
+        "body") 
+post.vars = 
+      c("author", "title", "created_utc", "name", "id", "subreddit_id",
+        "downs",  "ups", "upvote_ratio", "likes", "score", "num_comments",    
+        "permalink",  "url", "selftext")
+
+### recursive get comments function
+      get_children = function(parent){
+            if("" %in% parent$data$replies)   return(NULL)
+            parent$data$replies$data$children
+      }
+      get_reply_list <- function(parent.list){
+            if(is.null(parent.list)) return(NULL)
+            child.list = 
+                  lapply(parent.list, get_children) %>% 
+                  unlist(recursive=F) %>%
+                  get_reply_list()
+            c(child.list, parent.list)
+      }
+      get_comments <- function(file.json){
+            comments = list(file.json$data$children[[2]])
+            replies = 
+                  get_reply_list(comments) %>%
+                  lapply(function(x){
+                              if(length(x$data) < 10) NULL else x$data[comm.vars]
+                        })%>%
+                  do.call(what = rbind)
+            return(replies)
+      }
+      get_posts <- function(file.json){
+            file.json$data$children[[1]]$data[post.vars]
+      }
+      
+### get text for all posts in directory
+      data.dir = "Data/One_Day_Depression_Sample/depression 01-06-2016 30-06-2016/"
+      all.files = dir(data.dir)[grep("json", dir(data.dir))]
+
+      comm.data <- data.frame()
+      post.data <- data.frame()
+
+      for(file.name in all.files){
+            try({
+                  cat(file.name, "\n")
+                  file.json = 
+                        file.path(data.dir, file.name) %>%
+                        readLines() %>%
+                        fromJSON()
+                  comm.data <- rbind(comm.data, get_comments(file.json))
+                  post.data <- rbind(post.data, get_posts(file.json))
+            })
+      }
+      
+      rm(all.files, comm.vars, file.json, file.name, get_comments,
+         get_children, get_posts, get_reply_list, post.vars,
+         data.dir, bad.file)
+      save.image(file="Data/June_Posts.RData")
+

### 2016-10-13 Scripts/4.5_functions_scrape_reddit_comment.R

@@ -1,0 +1,58 @@
+
+library(httr)
+library(dplyr)
+
+### takes a list and replaces NULL values with NA values
+      replace_null <- function(a.list){
+            null.values <- unlist(lapply(a.list, is.null))
+            a.list[null.values] <- NA
+            return(a.list)
+      }
+
+### grabs data for a user
+      get_reddit_user <- function(username, type = "submitted", after=NA){
+          root_url = "https://api.reddit.com/user/"
+          url = paste0(root_url, username, "/", type)
+          if(!is.na(after)) url = paste0(url, "?after=", after)
+          agent2 = user_agent("blah")
+          reddit = GET(url, agent2)
+          stop_for_status(reddit)
+          cr = content(reddit)
+          return(cr)
+      }
+
+### grabs comments from user data
+      comm.vars =
+            c("author", "created_utc", "likes", "score", "ups", "downs", 
+              "subreddit_id", "link_id", "id", "name", "parent_id",        
+              "body") 
+      post.vars = 
+            c("author", "title", "created_utc", "name", "id", "subreddit_id",
+              "downs",  "ups", "upvote_ratio", "likes", "score", "num_comments",    
+              "permalink",  "url", "selftext")
+      
+      user_data_frame <- function(user, type="submitted", after = NA, n=0){
+            if(n==1000) return(NULL)
+            if(type == "submitted"){
+                  vars = post.vars
+            } else if(type=="comments"){
+                  vars = comm.vars
+            }
+            data.list = get_reddit_user(user, type, after)$data$children
+            data = 
+                  lapply(data.list, 
+                         function(x) {
+                               x$data[vars] %>%
+                               replace_null() %>%
+                               as.data.frame(stringsAsFactors=F)
+                         }) %>%
+                  do.call(what="rbind")
+            if(is.null(data)) return(NULL)
+            if(nrow(data) == 25){
+                  cat(n, ", ")
+                  next.data = 
+                        user_data_frame(user, type, after =  data$name[25], n = n+25)
+                  data = rbind(data, next.data)
+            }
+            return(data)
+      }

### 2016-10-13 Scripts/4_Scrape_User_Data.R

@@ -1,0 +1,24 @@
+
+### get functions
+      source(file="Scrape_User_Data/functions_scrape_reddit_comment.R")
+      load(file = "Data/June_Unique_SI_Authors.RData")
+      authors = na.omit(authors)
+      
+### loop through users
+      user.comment.data = data.frame()
+      user.post.data = data.frame()
+      
+for(user in authors){
+            cat("\nuser: ", user)
+            tryCatch({
+                  cat("\n\t submissions: ")
+                  user.submitted = user_data_frame(user, type="submitted")
+                  cat("\n\t comments: ")
+                  user.comments = user_data_frame(user, type="comments")
+                  user.comment.data = rbind(user.comment.data, user.comments)
+                  user.post.data = rbind(user.post.data, user.submitted)
+            }, error = function(e) {cat("\n\t error from user: ", user)})
+}
+rm(comm.vars, get_reddit_user, post.vars, replace_null, 
+   user, user_data_frame, user.comments, user.submitted)
+save.image(file = "Data/June_Authors_Data.RData")

### 2016-10-13 Scripts/5_Combine_Posts_Comments.R

@@ -1,0 +1,43 @@
+### Setup
+      load(file="Data/June_Authors_Data.RData")
+      rm(authors)
+      library(dplyr)
+      
+### Define Functions
+      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+      
+### Reformat Data
+      user.data = 
+            rbind(transmute(user.comment.data, author, subreddit_id,  
+                            date = get.date(created_utc), type="post",
+                            post = link_id, text = body),
+                  transmute(user.post.data, author, subreddit_id,  
+                            date = get.date(created_utc), type="comment",
+                            post = name, text = selftext)) %>%
+            mutate(r.depression = subreddit_id=="t5_2qqqf") %>%
+            group_by(author) %>%
+            arrange(date) %>%
+            mutate(time.last = c(NA, diff(date))) %>%
+            ungroup()
+      
+      rm(user.comment.data, user.post.data, get.date)
+      
+### Classify Suicide Ideation
+      source("Suicide_Classification_Algorithms/ideation_phrases.R")
+      
+      ### Get phrases
+            key.phrases = clean.text(key.phrases)
+            key.phrases = key.phrases[nchar(key.phrases) > 8]
+            key_phrase_regex = paste(key.phrases, collapse="|")
+            
+      ### Classify text
+            user.data$txt = clean.text(user.data$text)
+            user.data$class = grepl(key_phrase_regex, user.data$txt, ignore.case = T)
+            user.data$txt = NULL
+      
+      rm(list=setdiff(ls(), c("user.data")))
+            
+### Save New Data Frame
+      save(user.data, file="Data/June_Authors_Data_Classified.RData")
+      hist(user.data$time.last)
+      

### 2016-10-13 Scripts/Pretest/Assign_Pretest_Values.R

@@ -1,0 +1,18 @@
+pretest <- read.csv(file="Scrape_Reddits/pretest.csv", 
+                    header=F, stringsAsFactors=F)
+
+colnames(pretest) <- c("title", "subreddit", "author", "date", "link", "text")
+
+pretest <- cbind(pretest, suicidal=0, suicidal.past=0, mental.disorder=0)
+
+for(i in 1:nrow(pretest)){
+      print(pretest[i,"text"])
+      suicidal <- readline(prompt="Current Suicide Ideation (0,1):") 
+      suicidal.past <- readline(prompt="Past Suicide Ideation (0,1):") 
+      mental.disorder <- readline(prompt="Some Mental Disorder (0,1):") 
+      pretest[i,7:9] <- c(suicidal, suicidal.past, mental.disorder)
+}
+
+write.csv(pretest, file="Scrape_Reddits/classified_pretest.csv")
+
+

### 2016-10-13 Scripts/Suicide_Classification_Algorithms/Assign_Test_Values.R

@@ -1,0 +1,13 @@
+load(file="Data/Training_Lacey2.RData")
+
+for(i in 1:nrow(lacey2)){
+      writeLines(paste(lacey2[i,"title"],"\n",
+          lacey2[i,"post.text"], "\n",
+          lacey2[i,"suicidal"]))
+      lacey2$suicidal[i] <- readline(prompt="Current Suicide Ideation (0,1):") 
+}
+
+save(lacey2, file="Data/Training_Lacey2_Classified.RData")
+
+table(lacey2$suicidal)
+

### 2016-10-13 Scripts/Suicide_Classification_Algorithms/Classify_June.R

@@ -1,0 +1,22 @@
+
+load(file = "Data/June_Posts.RData")
+source("Suicide_Classification_Algorithms/ideation_phrases.R")
+
+### Get phrases
+      key.phrases = clean.text(key.phrases)
+      key.phrases = key.phrases[nchar(key.phrases) > 8]
+      key_phrase_regex = paste(key.phrases, collapse="|")
+
+### Classify text
+      comm.data$txt = clean.text(comm.data$body)
+      comm.data$class = grepl(key_phrase_regex, comm.data$txt, ignore.case = T)
+      comm.data$txt = NULL
+      
+      post.data$txt = clean.text(paste(post.data$title, post.data$selftext))
+      post.data$class = grepl(key_phrase_regex, post.data$txt, ignore.case = T)
+      post.data$txt = NULL
+      rm(list=setdiff(ls(), c("comm.data","post.data")))
+      
+save.image(file="Data/June_Posts_Classified.RData")
+      
+      

### 2016-10-13 Scripts/Suicide_Classification_Algorithms/Review_Classifier.R

@@ -1,0 +1,42 @@
+load(file="Data/Training/Training_Lacey_Classified.RData")
+load(file="Data/Training/Training_Lacey2_Classified.RData")
+load(file="Data/Training/Training_Linda_Classified.RData")
+load(file="Data/Training/Training_Linda_Classified2.RData")
+
+### Merge Data
+      df1 <- merge(lacey, linda, 
+                   by=c("author", "created", "title", 
+                        "link", "post.text", "file"),
+                   all=T, suffixes = c(".la", ".li"))
+      
+      df2 <- merge(lacey2, linda2, 
+                   by=c("author", "created", "title", 
+                        "link", "post.text", "file"),
+                   all=T, suffixes = c(".la", ".li"))
+      
+      df <- rbind(df1, df2)
+      rm(df1, df2, lacey, linda, linda2, lacey2)
+      
+### Fix bugs
+      df$suicidal.la[df$suicidal.la == ""] <- "0"
+      df$suicidal.la[is.na(df$suicidal.la)] <- "na"
+      df$suicidal.li[is.na(df$suicidal.li)] <- "na"
+      df$suicidal = df$suicidal.li == "1" | df$suicidal.la == "1" 
+      
+### Review Classifiers
+      source("Suicide_Classification_Algorithms/ideation_phrases.R")
+      load(file="Data/June_Posts.RData")
+      
+      ### Get phrases
+      key.phrases = clean.text(key.phrases)
+      key.phrases = key.phrases[nchar(key.phrases) > 8]
+      key_phrase_regex = paste(key.phrases, collapse="|")
+      
+      ### Classify text
+      comm.data$txt = clean.text(comm.data$body)
+      comm.data$class = grepl(key_phrase_regex, comm.data$txt, ignore.case = T)
+      
+      post.data$txt = clean.text(post.data$body)
+      post.data$class = grepl(key_phrase_regex, post.data$txt, ignore.case = T)
+      with(df, table(suicidal, class))
+      

### 2016-10-13 Scripts/Suicide_Classification_Algorithms/Split_Test_Training.R

@@ -1,0 +1,11 @@
+load(file="Data/Jun1_Post_Data.RData")
+
+all.ind <- sample(1:nrow(post.data), size = 1000, replace = F)
+lacey2 <- post.data[all.ind[1:300],]
+linda2 <- post.data[all.ind[200:499],]
+test2 <- post.data[all.ind[500:1000],]
+
+save(linda2, file="Data/Training_Linda2.RData")
+save(lacey2, file="Data/Training_Lacey2.RData")
+save(test2, file="Data/Test2.RData")
+

### 2016-10-13 Scripts/Suicide_Classification_Algorithms/ideation_phrases.R

@@ -1,0 +1,93 @@
+
+library(dplyr)
+
+### Clean text
+clean.text <-function(x){
+      x = gsub(" |\t|\n", "", x)
+      x = gsub("[[:punct:]]", "", x)
+      a = paste(word.list$accessories, collapse="|")
+      x = gsub(a, "", x)
+      return(tolower(x))
+}
+
+### Read in the suicide lexicon
+words <- readLines("Suicide_Classification_Algorithms/Suicide_Syntax.txt")
+words <- gsub("\t","",words)
+word.list <- list()
+category <- ""
+
+for(i in words){
+      if(grepl("\\[", i)){
+            category <- sub("\\[","",i)
+            category <- sub("\\]:","",category)
+            category <- sub(" ","_",category)
+            word.list[category] <- ""
+      } else word.list[[category]] <- append(word.list[[category]], i)
+}
+
+word.list <- lapply(word.list, function(x) x[-1])
+
+### Generate Suicidal Phrases
+make.phrases <- function(x, i){
+      sub(" \'", "\'", 
+      paste(i, 
+      expand.grid(word.list[x]) %>% 
+      apply(1, paste, collapse=" "))) 
+}
+
+### Direct admission of suicide ideation
+      # [iam] [intentioning verb] [suicide verb]
+      i.am.intentioningverb.suicideverb <- make.phrases(c("iam", "intentioning_verb", "suicide_verb"), i="")
+
+      #[I am] [thinking verb] [suicide noun]
+      i.am.thinkingverb.suicidenoun <- make.phrases(c("iam", "thinking_verb","suicide_noun"), i="")
+      
+      #I [intention verb] [suicide verb]
+      i.intentionverb.suicideverb <- make.phrases(c("intention_verb", "suicide_verb"), i="i")
+      
+      #I [possess] [think noun] [suicide noun]
+      i.possess.thinknoun.suicidenoun <- make.phrases(c("possess", "think_noun", "suicide_noun"), i="i")
+      
+      #I [think verb] [suicide noun]
+      i.thinkverb.suicidenoun <- make.phrases(c("think_verb", "suicide_noun"), i="i")
+      
+      #If I [suicide verb]
+      i.suicideverb <- make.phrases(c("suicide_verb"), i="i")
+      
+      #[iam] [suicide adj]
+      iam.suicideadjective <- make.phrases(c("iam", "suicide_adj"), i="")
+      
+      # me to [suicide verb]
[…]

### 2016-10-13 Scripts/0_Pretest_SI_Classification/Pretest_Summary.Rmd
renamed script files with order of operations. begining to amend file paths in scripts.

---
title: "Pretest Summary"
author: "Lacey Etzkorn"
date: "September 23, 2016"
output: 
      html_document:
            toc: TRUE
---

```{r setup, echo=FALSE}
### Set WD
      setwd("/Users/etzkornlacey15/Documents/Reddit_Suicide/Pretest/")
      library(dplyr)
### Load Pretest Data
      pretest.lacey <- read.csv(file="lacey_classified_pretest.csv",
                                stringsAsFactors = F)
      pretest.linda <- read.csv(file="linda_classified_pretest.csv", 
                                stringsAsFactors = F) %>%
            select(X, suicidal, suicidal.past, mental.disorder)
      pretest <- merge(pretest.lacey, pretest.linda, 
                       by = c("X"), suffixes=c(".lacey", ".linda"))
### Correct Misspecified Values
      bad0 <- c("00", "o", "")
      pretest$suicidal.lacey <- as.numeric(ifelse(pretest$suicidal.lacey %in% bad0, "0", pretest$suicidal.lacey))
      pretest$suicidal.linda <- as.numeric(ifelse(pretest$suicidal.linda %in% bad0, "0", pretest$suicidal.linda))
      pretest$suicidal.past.lacey <- as.numeric(ifelse(pretest$suicidal.past.lacey %in% bad0, 
                                            "0", pretest$suicidal.past.lacey))
      pretest$suicidal.past.linda <- as.numeric(ifelse(pretest$suicidal.past.linda %in% bad0, 
                                            "0", pretest$suicidal.past.linda))
```

# Correct Mistakes

```{r}
pretest <- mutate(pretest, 
                  suicidal = suicidal.linda + suicidal.lacey > 0,
                  suicidal.past = suicidal.past.linda + suicidal.past.lacey > 0,
                  mental.disorder = mental.disorder.linda + mental.disorder.lacey > 0) 
### Current
      pretest$suicidal[38] <- T
      pretest$suicidal[46] <- T 
      pretest$suicidal[55] <- F 
      pretest$suicidal[76] <- T 
      pretest$suicidal[95] <- T 
      pretest$suicidal[90] <- T

### Past
      pretest$suicidal.past[4] <- F 
      pretest$suicidal.past[31] <- F 
      pretest$suicidal.past[60] <- T 
      pretest$suicidal.past[95] <- T 
      pretest$suicidal.past[104] <- T

### Mental Condition
      pretest$mental.disorder[8] <- T
      pretest$mental.disorder[26] <- F
      pretest$mental.disorder[30] <- T
      pretest$mental.disorder[49] <- T
      pretest$mental.disorder[76] <- F
      pretest$mental.disorder[98] <- T
      pretest$mental.disorder[102] <- T
```

# Check Blanks

```{r}
prop.table(table(pretest$text ==""))
pretest <- filter(pretest, !pretest$text=="")
```

# Tabulate by Person

```{r}
      with(pretest, table(suicidal.linda, suicidal.lacey))
      with(pretest, table(suicidal.past.linda, suicidal.past.lacey))
      with(pretest, table(mental.disorder.linda, mental.disorder.lacey))
```

### Look at Posts by Reddit

```{r}

### Tabulate by Subreddit
      with(pretest, table(subreddit, suicidal))
      with(pretest, table(subreddit, suicidal.past))
      with(pretest, table(subreddit, mental.disorder))
      with(pretest, table(subreddit))

### Tabulate Outcomes
      with(pretest, table(suicidal, mental.disorder))
### Distribution of dates
      hist(pretest$date)
```

### Save Data

```{r}
pretest <- 
pretest %>% 
select(title,subreddit,author,date,text,suicidal,suicidal.past)
save(pretest, file="Pretest_Cleaned_Data.RData")
```

### 2016-10-13 Scripts/1_Read_JSON_Files.R

@@ -38,7 +38,7 @@ post.vars =
       }
       
 ### get text for all posts in directory
-      data.dir = "Data/One_Day_Depression_Sample/depression 01-06-2016 30-06-2016/"
+      data.dir = "Data/June_Depression_Sample/depression 01-06-2016 30-06-2016/"
       all.files = dir(data.dir)[grep("json", dir(data.dir))]
 
       comm.data <- data.frame()
@@ -59,5 +59,5 @@ post.vars =
       rm(all.files, comm.vars, file.json, file.name, get_comments,
          get_children, get_posts, get_reply_list, post.vars,
          data.dir, bad.file)
-      save.image(file="Data/June_Posts.RData")
+      save.image(file="Data/June_Depression_Sample/June_Posts.RData")
 

### 2016-10-18 Paper_Rough_Draft.Rmd
Added MC sampling.

---
title: "Paper"
author: "Lacey Etzkorn"
date: "October 13, 2016"
output: html_document
---

# Motivation

A problem that online forums and communities face is suicide. Numerous concerns have been raised over the impact that participating in online communities has on individual health, especially when the community surrounds issues of mental health and

It would benefit moderators of these online communities to be able to study the impact of their moderation policies have on the health of the community users.

In some instances, moderators have cited how seemingly benign policies have actually harmed the mental health of community users. For example, reddit moderator [name] cites the policy that they used to remove posts containing SI content in fear that the SI content would spread to others... [Re-Read suicide watch article]

Before moderators can evaluate the effect of a policy on mental health, it would benefit them to have a set of validated outcomes to measure their policies against. This is a difficult problem because many relevant health outcomes are not observable by internet community moderators. They only have posting information, and possibly login information. Things such as depression severity, other biomarkers, lifestyle factors, mortality, and even the outcome of suicide are not measurable from the moderator's perspective.

Some previous research has developed some outcomes that might be relevant to public health research. Choudhury et al. develop models for detecting and understanding user-specific shifts to and from suicidal ideation on reddit.

However, another outcome relevant to mental health board moderators might be the actual outcome of suicide since suicide might be a major problem in some internet communities. As far as we know, there is no published work on identifying suicides from online mental health board data.

This is probably because this is an impossible problem for which there is no data. However, it is still worth attempting to understand the best estimate we can get from this data. A next best option could be to estimate the rate at which users abandon their user accounts. A more tractable, intermediate outcome could be the identification of users who have stopped using reddit. This intermediate outcome of the users who have stopped using reddit must be a super-set of users who may have committed suicide. In this sense we can place an upper bound on the proportion of reddit users who actually commit suicide given the proportion of reddit users who stop using reddit.

# Methods

The identification of whether a user has stopped using reddit could be done using the user-specific distribution of times between posts. We can compare the time from data collection to the most recent post and compare this to the user-specific distribution of times between posts to get some sort of bayes estimate of whether the user has stopped using reddit.

After doing a brief literature review, it seems that studying mental health via social media is an emerging field. As far as we can tell, Munmun de Choudhury at Georgia Tech leads field of using social media to study mental health and online communities and social interactions. We have found a number of papers from her that will be especially pertinent to us as we continue our research. We will continue to look for papers from other authors in her citations.

To adress the first two questions, we scraped all available comment and post data from /r/depression for the month of June. The package [insert package] was used to scrape this data. The month June was chosen to ensure that we sould have three months of follow-up time for SI classified users. An earlier month wasn't chosen because Reddit censors user comment and post history to the most recent 1,000 comments and 1,000 posts each.

We then classified the text from each post and comment according to whether it contained SI evidence. Details of this classification process are described in a subsequent section. Then, we produced a list of unique user ids associated with any SI evidence. With this list, we then went back to the reddit API, and scraped the comment and post history for each user.

### SI Classification

Our goal four our SI classification algorithm was to produce a set of comments that almost certainly contained only true SI comments. Hence, we set out to maximize specificity while throwing sensitivity out the window. While we recognize that could be many algorithms better suited for our final goal of estimating the incidence of suicide in our population, we were fine to just make something that worked for now.

[Definition of Suicidal Ideation]

We began by reading through a sample of 100 randomly selected comments from various mental health subreddits to get a sense of how people expressed suicidal ideation on Reddit in general. From each of the SI comments from this 100, we extracted the smallest phrase(s) that contained evidence of SI. Examples of these phrase bits include:

* "I think about suicide"
* "I just don't want to live""
* "I have struggled with depression and suicidal thoughts"
* "my suicide plan"
* "I still feel like blowing my brains out"

We then categoized these phrases into 12 linguistically distinct modes of expressing SI, adding extra where we felt appropriate:

Intention to, or thoughts of suicide/dying:
* [I am] [intending to] [suicide verb]
* [I am] [thinking about] [suicide noun]
* I [intend to] [suicide verb]
* I [suicide verb]
* [I am] [suicide adjective]
* Why not [suicide verb]
* I [think about] [suicide noun]
* I [think]
* me [suicide verb]
* me [suicide noun]

Oppose life:
* [I] [oppose] [live noun]
* [I] [am opposed to] [living]

For each of these modes of SI expression, we generated all possible combinations of words for each category to get all possible phrases for that mode. For example, to generate all possible phrases for  "I [intend to] [suicide verb]", we combined the "intend to" verbs

      want to, were to, would like to, wish to, decided to, decide to, am not afraid to, am not scared to, have to, had to, try to, tried to, would like to, can, will, must, might, should, could, intend to, intended to, have come to, 've come to, ‘d like to, ‘d, ‘ll

with the suicide verbs

      die, commit suicide, kill myself, off myself, end my life, no longer be here, take some pills, leave this world, end it, blow my brains out, kicked the bucket, kick the bucket, cut my throat, hang myself

After all phrases for all 12 modes of SI expression have been generated, we remove all punctuation and spacing from both the post text and the phrase text. We combine all phrases into a regular expression using the or "|" operator, and then use the function "grepl" to test whether each post contains any phrase.

### Estimation

# Results

### June /r/depression

For the month of June, /r/depression contained [n] posts, representing contributions from [n] authors. We identified [n] comments with SI evidence from [n] unique users.

In a sample of 100 SI-positive posts, [n] did not have true SI evidence. In a sample of 100 SI-negative posts, [n] did have SI evidence.

### User Follow-Up

After scraping the post history for each of the SI-positive users, we find no post or comment data for [n] users, and we find [n] users whose comments and posts were censored by June. We are then left with [n] users.

# Discussion

Online communities present a unique platform where people can address their own mental health concerns.

A online community such as the depression subreddit provides a unique opportunity for researchers to glimpse into the thoughts of people with depression outside of a clinical setting. The depression subreddit is a public community where users do not need to present any identifiable information.

### Limitations

For this method, we only incorporate user specific information as the time between posts. However, a number of other factors might give us information about whether a user actually attempts suicide. Sentiment might matter. Recent SI posts might matter. Actual suicide notes might matter.

We do not differentiate between suicidal ideation and suicide notes.

We also cannot observe unsuccessful suicide attempts.

### Future Direction

In order to get a working lower-bound on reddit drop-out, it may be good to run this method on sample of users from non-mental-health-related subreddits in june to get a sense of general rates of reddit-drop-out. We might then be able to then take the difference in rate of drop out among SI-positive users and SI-negative users to estimate the depression+SI attributable drop out rate.

# Works Cited

* Discovering Shifts to Suicidal Ideation from Mental Health Content in Social Media (2016) http://www.munmund.net/pubs/chi16_SuicidalIdeation.pdf

* Social Media as a Measurement Tool of Depression in Populations (2013) http://www.munmund.net/pubs/websci_13.pdf

* Predicting Postpartum Changes in Emotion and Behavior via Social Media (2013) http://www.munmund.net/pubs/chi_13.pdf

* Not All Moods are Created Equal! Exploring Human Emotional States in Social Media (2012) http://www.munmund.net/pubs/icwsm_12_1.pdf

* Happy, Nervous or Surprised? Classification of Human Affective States in Social Media (2011) http://www.munmund.net/pubs/icwsm_12_2.pdf

* Recovery Amid Pro-Anorexia: Analysis of Recovery in Social Media (2016) http://www.munmund.net/pubs/chi16_TumblrRecovery.pdf

### 2016-10-18 Scripts/1_Read_JSON_Files.R

@@ -1,4 +1,5 @@
 library(dplyr)
+library(jsonlite)
 
 ### variable names
 comm.vars =

### 2016-10-18 Scripts/2_Combine_June_Posts_Comments.R

@@ -1,0 +1,36 @@
+### Setup
+      load(file="Data/June_Depression_Sample/June_Posts.RData")
+      library(dplyr)
+      
+### Define Functions
+      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+      
+### Reformat Data
+      comm.data =
+            transmute(comm.data, author, created_utc, date = get.date(created_utc), 
+                      thread_id = link_id, text = body)
+      post.data = 
+            transmute(post.data, author, created_utc, date = get.date(created_utc),
+                      thread_id = name, text = paste(title, selftext))
+      user.data = 
+            rbind(comm.data, post.data)
+      
+      rm(comm.data, post.data, get.date)
+      
+### Classify Suicide Ideation
+      source("Scripts/2.2_SI_Classification/ideation_phrases.R")
+      
+      ### Get phrases
+            key.phrases = clean.text(key.phrases)
+            key.phrases = key.phrases[nchar(key.phrases) > 8]
+            key_phrase_regex = paste(key.phrases, collapse="|")
+            
+      ### Classify text
+            user.data$txt = clean.text(user.data$text)
+            user.data$si = grepl(key_phrase_regex, user.data$txt, ignore.case = T)
+            user.data$txt = NULL
+      
+      rm(list=setdiff(ls(), c("user.data")))
+            
+### Save New Data Frame
+      save(user.data, file="Data/June_Depression_Sample/June_Posts_Classified.RData")

### 2016-10-18 Scripts/5_Classify_SI_Author_Data.R

@@ -1,4 +1,3 @@
-
 load(file = "Data/June_Posts.RData")
 source("Suicide_Classification_Algorithms/ideation_phrases.R")
 

### 2016-10-18 Scripts/5_Combine_Posts_Comments.R

@@ -1,43 +1,0 @@
-### Setup
-      load(file="Data/June_Authors_Data.RData")
-      rm(authors)
-      library(dplyr)
-      
-### Define Functions
-      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
-      
-### Reformat Data
-      user.data = 
-            rbind(transmute(user.comment.data, author, subreddit_id,  
-                            date = get.date(created_utc), type="post",
-                            post = link_id, text = body),
-                  transmute(user.post.data, author, subreddit_id,  
-                            date = get.date(created_utc), type="comment",
-                            post = name, text = selftext)) %>%
-            mutate(r.depression = subreddit_id=="t5_2qqqf") %>%
-            group_by(author) %>%
-            arrange(date) %>%
-            mutate(time.last = c(NA, diff(date))) %>%
-            ungroup()
-      
-      rm(user.comment.data, user.post.data, get.date)
-      
-### Classify Suicide Ideation
-      source("Suicide_Classification_Algorithms/ideation_phrases.R")
-      
-      ### Get phrases
-            key.phrases = clean.text(key.phrases)
-            key.phrases = key.phrases[nchar(key.phrases) > 8]
-            key_phrase_regex = paste(key.phrases, collapse="|")
-            
-      ### Classify text
-            user.data$txt = clean.text(user.data$text)
-            user.data$class = grepl(key_phrase_regex, user.data$txt, ignore.case = T)
-            user.data$txt = NULL
-      
-      rm(list=setdiff(ls(), c("user.data")))
-            
-### Save New Data Frame
-      save(user.data, file="Data/June_Authors_Data_Classified.RData")
-      hist(user.data$time.last)
-      

### 2016-10-18 Scripts/6_MCMC.R

@@ -1,0 +1,40 @@
+
+### Load Data
+      load(file = "Data/SI_Author_Sample/Author_Summary.RData")
+      library(ggplot2)
+      library(reshape2)
+      user.summary = 
+            filter(user.summary, recent < 150) %>%
+            mutate(t = recent)
+      n = user.summary$n
+      eps = user.summary$eps
+      eps[is.na(eps)] = 0 
+      t = user.summary$t
+      N = nrow(user.summary)
+      
+### Simulate Mu given Data
+      alpha = 1; beta = 1
+      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
+      dim(mu)
+
+### Calculate P(Q) from Mu and data
+      prior.p = c(0.5, 10^-(1:4))
+      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
+      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
+      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
+      user.summary2 = 
+            cbind(user.summary, post_p) %>%
+            select(-recent) %>%
+            melt(id.vars = c("author", "n", "eps", "t"),
+                 value.name = "post.p", variable.name = "prior.p")
+      ggplot(user.summary2) + 
+            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
+            facet_wrap("prior.p") + 
+            theme_bw()
+
+### Now get overall credible interval for sum(Q)
+      prior.p = 0.000001
+      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
+      post.E = colSums(apply(mu, 2, make.p, p=prior.p))
+      hist(post.E, main = "Posterior Distribution for \n Expected Total Reddit Drop-Outs")
+      

### 2016-10-18 Scripts/SI_Classification/ideation_phrases.R

@@ -11,7 +11,7 @@ clean.text <-function(x){
 }
 
 ### Read in the suicide lexicon
-words <- readLines("Suicide_Classification_Algorithms/Suicide_Syntax.txt")
+words <- readLines("Scripts/2.2_SI_Classification/Suicide_Syntax.txt")
 words <- gsub("\t","",words)
 word.list <- list()
 category <- ""

### 2016-10-18 Scripts/Summarize_Author_Data.R

@@ -1,0 +1,30 @@
+
+### Load Data
+      load(file="Data/SI_Author_Sample/June_Authors_Data_Classified.RData")
+      colnames(user.data)
+      library(dplyr)
+      library(ggplot2)
+      
+### Summarize Data Frame
+      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+      oct10 = get.date("2016-10-10 16:00:00")
+      user.summary = 
+            user.data %>%
+            group_by(author) %>%
+            summarise(n = n()-1,
+                      eps = mean(time.last/60/60/24, na.rm=T),
+                      recent = as.numeric(oct10 - max(date)))
+      
+### Save Data
+      save(user.summary, file = "Data/SI_Author_Sample/Author_Summary.RData")
+      
+      
+      ggplot(user.summary) +
+            geom_histogram(aes(x=recent))
+      ggplot(user.summary) +
+            geom_histogram(aes(x=n))
+      ggplot(user.summary) +
+            geom_histogram(aes(x=eps))
+      
+      
+      #filter(user.summary, recent > 135)

### 2016-10-18 Paper_Rough_Draft.Rmd
Rough draft edits
added code and figure and more text to rough draft.

@@
 ---
-title: "Paper"
+title: "Do Reddit /r/depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates?"
 author: "Lacey Etzkorn"
-date: "October 13, 2016"
-output: html_document
+date: "October 18, 2016"
+output: 
+      html_document:
+            toc: TRUE
 ---
+
+```{r setup, include=FALSE}
+require(ggplot2); require(dplyr); require(reshape2)
+options(width = 90)
+options(digits = 4)
+```
 
@@
 
-A problem that online forums and communities face is suicide.
-Numerous concerns have been raised over the impact that participating in online communities has on individual health, especially when the community surrounds issues of mental health and
+The problem of suicide plagues social media and online communities devoted to mental health. [add context]
 
-It would benefit moderators of these online communities to be able to study the impact of their moderation policies have on the health of the community users.
+Social media has also learned to fight back. [add context]
 
-In some instances, moderators have cited how seemingly benign policies have actually harmed the mental health of community users.
-For example, reddit moderator [name] cites the policy that they used to remove posts containing SI content in fear that the SI content would spread to others...
-[Re-Read suicide watch article]
+Given the delicate relationship between social media and suicide, it is of utmost importance that community moderators study the impacts of their policies on their community's risk of suicide.
+There are numerous stories of how seemingly benign changes in community moderation policies have exacerbated user's poor mental health status.
+For example, [give example].
 
-Before moderators can evaluate the effect of a policy on mental health, it would benefit them to have a set of validated outcomes to measure their policies against.
-This is a difficult problem because many relevant health outcomes are not observable by internet community moderators.
-They only have posting information, and possibly login information.
-Things such as depression severity, other biomarkers, lifestyle factors, mortality, and even the outcome of suicide are not measurable from the moderator's perspective.
+Currently, moderators do not have data-intensive tools to evaluate the impact of policies on suicide risk.
+[Do they?].
+This is due, in part, to the lack of data available to moderators.
+In most cases, it is impossible for moderators to observe actual outcomes of suicide, especially when users are anonymous.
+Surrogate outcomes for suicide are currently in development.
+For example, Munmun de Choudhury uses [linguistic machine learning methods] to identify and predict user-specific shifts from discussing poor mental health to discussing suicide ideation.
+However, detecting suicidal ideation in user posts has limited utility when the desired outcome is a rate of suicide.
 
-Some previous research has developed some outcomes that might be relevant to public health research.
-Choudhury et al.
-develop models for detecting and understanding user-specific shifts to and from suicidal ideation on reddit.
-
-However, another outcome relevant to mental health board moderators might be the actual outcome of suicide since suicide might be a major problem in some internet communities.
-As far as we know, there is no published work on identifying suicides from online mental health board data.
-
-This is probably because this is an impossible problem for which there is no data.
-However, it is still worth attempting to understand the best estimate we can get from this data.
-A next best option could be to estimate the rate at which users abandon their user accounts.
-A more tractable, intermediate outcome could be the identification of users who have stopped using reddit.
-This intermediate outcome of the users who have stopped using reddit must be a super-set of users who may have committed suicide.
-In this sense we can place an upper bound on the proportion of reddit users who actually commit suicide given the proportion of reddit users who stop using reddit.
+In this paper, we propose a more direct method for estimating rates of suicide from social media data.
+[Do we actually do this?] We do this by estimating the rate at which users who admit to having suicidal ideation (SI) stop posting on Reddit.
+We then compare the drop-out rates between SI-positive and SI-negative users.
+Though our method is thoroughly problematic in its current state, we believe that, with a proper amount of statistical development and validation, it has the potential to become a decent measure of suicide rates in online mental health communities.
 
@@
 
-The identification of whether a user has stopped using reddit could be done using the user-specific distribution of times between posts.
-We can compare the time from data collection to the most recent post and compare this to the user-specific distribution of times between posts to get some sort of bayes estimate of whether the user has stopped using reddit.
+[give methods overview]
 
-After doing a brief literature review, it seems that studying mental health via social media is an emerging field.
-As far as we can tell, Munmun de Choudhury at Georgia Tech leads field of using social media to study mental health and online communities and social interactions.
-We have found a number of papers from her that will be especially pertinent to us as we continue our research.
-We will continue to look for papers from other authors in her citations.
+### Data
 
-To adress the first two questions, we scraped all available comment and post data from /r/depression for the month of June.
-The package [insert package] was used to scrape this data.
-The month June was chosen to ensure that we sould have three months of follow-up time for SI classified users.
-An earlier month wasn't chosen because Reddit censors user comment and post history to the most recent 1,000 comments and 1,000 posts each.
+Our target population is Reddit authors who post in the subreddit /r/depression in the month of June.
+Hence, we scrape all available (as of October 10, 2016) comment and post data from /r/depression for the month of June using the python package [insert package].
+The month June was chosen to ensure that we have at least three months of follow-up time for each author.
+An earlier month wasn't chosen because Reddit censors author comment and post history to the most recent 1,000 items each.
+Henceforth we will refer to comments and posts collectively as posts.
 
-We then classified the text from each post and comment according to whether it contained SI evidence.
+We then identified whether the text from each post contained evidence of suicidal ideation (SI) according to our classification algorithm.
 Details of this classification process are described in a subsequent section.
-Then, we produced a list of unique user ids associated with any SI evidence.
-With this list, we then went back to the reddit API, and scraped the comment and post history for each user.
+Then, we produced one list of unique author ids associated with any SI evidence as well as one equal-sized list of unique authors without any SI evidence.
+We then scraped the post history for both lists of authors and identified posts with SI evidence.
+
+### Estimation of Drop-Out Rates
+
+First, we assume that the posting histories of each author are a Poisson Process, and so times between posts are exponentially distributed with some author-specific mean $mu_i$ where $i$ indexes the authors.
+For each $\mu_i$, we can specify the prior distribution $1/\mu_i \sim gamma(1,1)$.
+Hence the posterior for $\mu_i$ is $1/\mu_i|n,\bar{\epsilon} \sim gamma(1 + n, 1 + n\cdot\bar{\epsilon})$, where n is the author's number of intervals between posts, and $\bar{\epsilon}$ is the user-specific average time between posts.
+
+Now if we specify a prior probability that any author drops out of reddit $\rho$, we can then directly calculate the posterior distribution of the probability they dropped out from the monte-carlo samples above.
+Let $t_i$ be the time between data collection and the most recent post for user $i$.
+This variable can be thought of the "censoring time".
+Then, the posterior probability that a user quits given their true time between posts is:
+$$ p_i|\mu_i   =   \frac{\rho} {e^{-\mu_i\cdot t_i} \cdot (1-\rho) + \rho} $$ 
+With this expression, we can transoform the monte-carlo samples from the posterior of $\mu_i$ to monte-carlo samples from the posterior of $p_i$.
+
+Finally, we can get the posterior distribution of the expected number of Reddit drop-outs.
+If $Q_i$ is the indicator that user $i$ has dropped out, then $E(\sum Q_i | p_1, p_2 ...) = E(\sum p_i | p_1, p_2 ...)$.
+
+Using this method, we generate monte-carlo samples from the posterior distribution for the expected number of drop-outs among SI-positive authors and SI-negative authors each.
+We can then compare these posteriors to get a sense of the number of excess reddit drop-outs that could be linked to suicide, or at least suicidal ideation.
 
@@
 
-### Estimation
-
 # Results
@@
 
-For the month of June, /r/depression contained [n] posts, representing contributions from [n] authors. We identified [n] comments with SI evidence from [n] unique users.
+For the month of June, /r/depression contained 22,041 posts, representing contributions from 7,572 authors. We identified 547 SI-positive posts from 492 unique users.
 
@@
 
-After scraping the post history for each of the SI-positive users, we find no post or comment data for [n] users, and we find [n] users whose comments and posts were censored by June.
-We are then left with [n] users.
+```{r , echo=FALSE, message=FALSE, warning=FALSE}
+load(file="Data/SI_Author_Sample/June_Authors_Data_Classified.RData")
+author.sum =
+      user.data %>%
+      group_by(author, type) %>%
+      summarise(oldest = min(date),
+                prop.dep.post = mean(r.depression, na.rm=T),
+                n.post = n()) 
+author.sum2 = 
+      user.data %>% 
+      group_by(author) %>%
+      summarise(oldest = min(date, na.rm=T),
+                newest = max(date, na.rm=T),
+                prop.dep.post = mean(r.depression, na.rm=T),
+                n_si = sum(class, na.rm=T),
+                n.post = n())
+user.data = 
+      transmute(author.sum2, author, 
+                rank_oldest = rank(oldest),
+                rank_newest = rank(newest),
+                rank_n = rank(n.post,ties.method = "random"),
+                rank_prop = rank(prop.dep.post,ties.method = "random")) %>%
+      merge(user.data, by = "author", all.y=T)
+user.data$point.label = 
+      ifelse(user.data$class, "SI",
+      ifelse(user.data$r.depression, "/r/depression","other")) %>%
+      ordered(labels = c("other", "/r/depression", "SI"))
+
+get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+july1 = get.date("2016-07-01 00:00:00")
+june1 = get.date("2016-06-01 00:00:00")
+jan1 = get.date("2016-01-01 00:00:00")
+ggplot() +
+geom_point(data = subset(user.data, date > jan1),
+           aes(y=rank_newest,x=date, 
+               color=point.label, alpha=point.label, 
+               size=point.label)) + 
+ggtitle("Distribution of Post Dates across Authors\nbetween Jan. and Oct.") +
+ylab("Author Rank by Newest Post") + xlab("Date") +
+geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.3) + 
+geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.3) + 
+scale_colour_manual(values = c("grey","darkblue", "red")) + 
+scale_size_manual(values = c(0.1,0.1,0.3)) + 
+scale_alpha_manual(values = c(0.1,0.1,1)) + 
+theme_bw()
+```
+
+After scraping the post history for each of the SI-positive users, we find no post or comment data for 1 author, and we find 16 authors whose full history was not available back to April 2016.
+We are left with 475 authors.
+
+The post histories for our 475 authors are depicted above.
+Each y value represents a unique author id, sorted by the time of their most recent post.
+Each x value represents the date of a post.
+Hence, we can read each horizontal line on this plot as the post history of one author.
+Red points represent SI-positive posts.
+Blue points represent posts in the /r/depression subreddit.
+Grey posts represent posts elsewhere on reddit.
+There a number of important features in this plot.
+First, we note that those authors who posted more recently tended to post more often, which is expected.
+Second we see that many authors made multiple SI-positive posts.
+Third, we see that nearly 170 of our 475 authors had their last post in June, which was the period that we used to sample from.
+Fourth, of these 170 authors, many did not post frequently before dropping-off reddit.
+However, a hand-full of them had posted frequently, and their drop-put is therefore suspicious.
+
+### Drop-Out Rate Estimates
+
+The histogram below represents the posterior distribution for the rate of drop-outs for authors whose June /r/depression comments were SI-positive.
+
+```{r, echo=FALSE, warning=FALSE}
+### Load Data
+      load(file = "Data/SI_Author_Sample/Author_Summary.RData")
+      user.summary = 
+            filter(user.summary, recent < 150) %>%
+            mutate(t = recent)
+      n = user.summary$n
+      eps = user.summary$eps
+      eps[is.na(eps)] = 0 
+      t = user.summary$t
+      N = nrow(user.summary)
+### Simulate Mu given Data
+      alpha = 1; beta = 1
+      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
+### Now get overall credible interval for sum(Q)
+      prior.p = 0.000001
+      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
+      post.E = colSums(apply(mu, 2, make.p, p=prior.p))/N * 100
+      hist(post.E, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
+           xlab="", ylab="")
+      ci = quantile(post.E, probs = c(0.025, 0.975))
+```
+
+Our 95% credible interval is (`r ci`), meaning there is a 95% probability that the expected rate of drop-out is between `r ci[1]` and `r ci[2]`.
+
+### Sensitivity to Priors
+
+We found that our conclusions were highly sensitive to our specified prior probability of drop-outs.
+
+```{r, echo=FALSE, warning=FALSE}
+### Calculate P(Q) from Mu and data
+      prior.p = c(0.5, 10^-(1:4))
+      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
+      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
+      user.summary2 = 
+            cbind(user.summary, post_p) %>%
+            select(-recent) %>%
+            melt(id.vars = c("author", "n", "eps", "t"),
+                 value.name = "post.p", variable.name = "prior.p")
+      ggplot(user.summary2) + 
+            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
+            facet_wrap("prior.p") + 
+            theme_bw() + 
+            xlab("Average Days between Posts") +
+            ylab("Days since Most Recent Post")
+```
 
@@
 
-### Future Direction
-
-In order to get a working lower-bound on reddit drop-out, it may be good to run this method on sample of users from non-mental-health-related subreddits in june to get a sense of general rates of reddit-drop-out.
-We might then be able to then take the difference in rate of drop out among SI-positive users and SI-negative users to estimate the depression+SI attributable drop out rate.
-
 # Works Cited
@@
 
-* Not All Moods are Created Equal! Exploring Human Emotional States in Social Media (2012) http://www.munmund.net/pubs/icwsm_12_1.pdf
-
-* Happy, Nervous or Surprised? Classification of Human Affective States in Social Media (2011) http://www.munmund.net/pubs/icwsm_12_2.pdf
-
-* Recovery Amid Pro-Anorexia: Analysis of Recovery in Social Media (2016) http://www.munmund.net/pubs/chi16_TumblrRecovery.pdf
+* Social Media Embraces Suicide Prevention CMAJ August 11, 2015 vol. 187 no. 11 First published June 29, 2015, doi: 10.1503/cmaj.109-5104 http://www.cmaj.ca/content/187/11/E333.short

### 2016-10-21 Paper_Rough_Draft.Rmd
edited rough draft

@@
 
-# Motivation
+# Introduction
 
@@
 
+The objective of our project is to quantify the risk of suicide for /r/depression authors. However, this objective is impossible for a number of reasons.
+
+Given that the desired objective is impossible, we set out to estimate a reasonable surrogate parameter that will still be useful to online community moderators.
+Hence, we define the following parameter.
+
+The difference in rate of dropouts
+
+The goal of our analysis is to estimate the difference in drop out rates between Reddit /r/depression authors who express suicidal ideation and /r/depression authors who don't
+
 ### Data
@@
 Our target population is Reddit authors who post in the subreddit /r/depression in the month of June.
-Hence, we scrape all available (as of October 10, 2016) comment and post data from /r/depression for the month of June using the python package [insert package].
+Hence, we scrape all available (as of October 10, 2016) comment and post data from /r/depression for the month of June using the python package subredditarchive.
 The month June was chosen to ensure that we have at least three months of follow-up time for each author.
@@
 
-First, we assume that the posting histories of each author are a Poisson Process, and so times between posts are exponentially distributed with some author-specific mean $mu_i$ where $i$ indexes the authors.
+Our goal is to estimate the expected rate at which SI-positive and SI-negative authors stop using Reddit.
+Ultimately, we will compare our estimated rates between these two groups to determine if there is some association between suicidal ideation and risk of dropping-out.
+
+First, we estimate the author-specific average time between posts $mu_i$, where $i$ indexes the authors.
+We assume that the post histories of each author are a Poisson process, and so observed times between posts are exponentially distributed with mean $mu_i$.
 For each $\mu_i$, we can specify the prior distribution $1/\mu_i \sim gamma(1,1)$.
@@
 
-Now if we specify a prior probability that any author drops out of reddit $\rho$, we can then directly calculate the posterior distribution of the probability they dropped out from the monte-carlo samples above.
+From each $mu_i$, we are able to calculate the probability that the author has stopped using Reddit.
+Let $\rho$ be the prior probability that any author drops out of Reddit.
 Let $t_i$ be the time between data collection and the most recent post for user $i$.
@@
 
-Finally, we can get the posterior distribution of the expected number of Reddit drop-outs.
-If $Q_i$ is the indicator that user $i$ has dropped out, then $E(\sum Q_i | p_1, p_2 ...) = E(\sum p_i | p_1, p_2 ...)$.
+Finally, we can calculate the posterior distribution of the expected number of Reddit drop-outs.
+If $Q_i$ is the indicator that user $i$ has dropped out, then $E(\sum Q_i \Big | p_1, p_2 ...) = E(\sum p_i \Big | p_1, p_2 ...)$.
 
 Using this method, we generate monte-carlo samples from the posterior distribution for the expected number of drop-outs among SI-positive authors and SI-negative authors each.
-We can then compare these posteriors to get a sense of the number of excess reddit drop-outs that could be linked to suicide, or at least suicidal ideation.
+We can then compare these posteriors to get a sense of the number of excess Reddit drop-outs associated with suicidal ideation.
 
@@
 
-Our goal four our SI classification algorithm was to produce a set of comments that almost certainly contained only true SI comments.
+Our goal for our SI classification algorithm was to produce a set of comments that almost certainly contained only true SI comments.
 Hence, we set out to maximize specificity while throwing sensitivity out the window.
@@
 Blue points represent posts in the /r/depression subreddit.
-Grey posts represent posts elsewhere on reddit.
+Grey posts represent posts elsewhere on Reddit.
 There a number of important features in this plot.
@@
 Third, we see that nearly 170 of our 475 authors had their last post in June, which was the period that we used to sample from.
-Fourth, of these 170 authors, many did not post frequently before dropping-off reddit.
+Fourth, of these 170 authors, many did not post frequently before dropping-off Reddit.
 However, a hand-full of them had posted frequently, and their drop-put is therefore suspicious.

### 2016-10-24 Paper_Rough_Draft.Rmd
Finalize EDA
Reran classifier on authors data summary. Added authors without SI.

@@
 options(digits = 4)
+load("June_Authors_Combined.RData")
 ```
@@
 The objective of our project is to quantify the risk of suicide for /r/depression authors. However, this objective is impossible for a number of reasons.
+
+Another potential es
 
@@
 ```{r , echo=FALSE, message=FALSE, warning=FALSE}
-load(file="Data/SI_Author_Sample/June_Authors_Data_Classified.RData")
-author.sum =
-      user.data %>%
-      group_by(author, type) %>%
-      summarise(oldest = min(date),
-                prop.dep.post = mean(r.depression, na.rm=T),
-                n.post = n()) 
-author.sum2 = 
-      user.data %>% 
+user.data = 
+      author.summary %>%
       group_by(author) %>%
-      summarise(oldest = min(date, na.rm=T),
-                newest = max(date, na.rm=T),
-                prop.dep.post = mean(r.depression, na.rm=T),
-                n_si = sum(class, na.rm=T),
-                n.post = n())
-user.data = 
-      transmute(author.sum2, author, 
-                rank_oldest = rank(oldest),
-                rank_newest = rank(newest),
-                rank_n = rank(n.post,ties.method = "random"),
-                rank_prop = rank(prop.dep.post,ties.method = "random")) %>%
+      filter(newest == max(newest)) %>%
+      ungroup %>%
+      group_by(si.author)%>%
+      transmute(author, rank_newest = rank(newest)) %>%
+      ungroup %>%
+      select(-si.author) %>%
       merge(user.data, by = "author", all.y=T)
@@
       ordered(labels = c("other", "/r/depression", "SI"))
-
-get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
-july1 = get.date("2016-07-01 00:00:00")
-june1 = get.date("2016-06-01 00:00:00")
-jan1 = get.date("2016-01-01 00:00:00")
-ggplot() +
-geom_point(data = subset(user.data, date > jan1),
-           aes(y=rank_newest,x=date, 
+user.data$si.group = 
+      ifelse(user.data$si.author, "SI-Positive in June /r/depression",
+             "SI-Negative in June /r/depression")
+### Make plot
+ggplot(data = subset(user.data, date > jan1)) +
+geom_point(aes(y=rank_newest,x=date, 
                color=point.label, alpha=point.label, 
@@
 scale_alpha_manual(values = c(0.1,0.1,1)) + 
-theme_bw()
+theme_bw() + facet_wrap("si.group")
 ```

### 2016-10-24 Scripts/2_Combine_June_Posts_Comments.R

@@ -1,5 +1,5 @@
 ### Setup
-      load(file="Data/June_Depression_Sample/June_Posts.RData")
+      load(file="Data/June_NoSI_Authors_Data.RData")
       library(dplyr)
       
 ### Define Functions

### 2016-10-24 Scripts/3.1_Scrape_User_Data.R

@@ -1,0 +1,24 @@
+
+### get functions
+      source(file="Scripts/functions_scrape_reddit_comment.R")
+      load(file = "Data/June_Depression_Sample/June_Unique_NoSI_Authors.RData")
+      authors.noSI = na.omit(authors.noSI)
+      
+### loop through users
+      user.comment.data = data.frame()
+      user.post.data = data.frame()
+      
+for(user in authors.noSI){
+            cat("\nuser: ", user)
+            tryCatch({
+                  cat("\n\t submissions: ")
+                  user.submitted = user_data_frame(user, type="submitted")
+                  cat("\n\t comments: ")
+                  user.comments = user_data_frame(user, type="comments")
+                  user.comment.data = rbind(user.comment.data, user.comments)
+                  user.post.data = rbind(user.post.data, user.submitted)
+            }, error = function(e) {cat("\n\t error from user: ", user)})
+}
+rm(comm.vars, get_reddit_user, post.vars, replace_null, 
+   user, user_data_frame, user.comments, user.submitted)
+save.image(file = "Data/June_NoSI_Authors_Data.RData")

### 2016-10-24 Scripts/4.1_Classify_SI_Author_Data.R

@@ -1,0 +1,43 @@
+load(file = "Data/SI_Author_Sample/June_Authors_Data.RData")
+
+get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+october10 = get.date("2016-10-10 16:00:00")
+
+user.comment.data =
+      transmute(user.comment.data, 
+                author, subreddit_id, date = get.date(created_utc), type="comment",
+                post = link_id, text = body, r.depression = subreddit_id=="t5_2qqqf") %>%
+      filter(date < october10) %>%
+      group_by(author) %>%
+      arrange(date) %>%
+      mutate(time.last = c(NA, diff(date))/60/60/24) %>%
+      ungroup
+
+user.post.data = 
+      transmute(user.post.data,
+                author, subreddit_id, date = get.date(created_utc), type="post",
+                post = name, text = paste(title, selftext), r.depression = subreddit_id=="t5_2qqqf") %>%
+      filter(date < october10) %>%
+      group_by(author) %>%
+      arrange(date) %>%
+      mutate(time.last = c(NA, diff(date))/60/60/24) %>%
+      ungroup
+
+user.data = 
+      rbind(user.post.data, user.comment.data)
+
+### Get phrases
+source("Scripts/SI_Classification/ideation_phrases.R")
+      key.phrases = clean.text(key.phrases)
+      key.phrases = key.phrases[nchar(key.phrases) > 8]
+      key_phrase_regex = paste(key.phrases, collapse="|")
+
+### Classify text
+      user.data$txt = clean.text(user.data$text)
+      user.data$class = grepl(key_phrase_regex, user.data$txt, ignore.case = T)
+      user.data$txt = NULL
+      rm(list=setdiff(ls(), c("user.data")))
+      
+save.image(file="Data/SI_Author_Sample/June_SI_Classified.RData")
+      
+      

### 2016-10-24 Scripts/4.2_Classify_NoSI_Author_Data.R

@@ -1,0 +1,43 @@
+load(file = "Data/SI_Author_Sample/June_NoSI_Authors_Data.RData")
+get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+october10 = get.date("2016-10-10 16:00:00")
+
+user.comment.data =
+            transmute(user.comment.data, 
+                      author, subreddit_id, date = get.date(created_utc), type="comment",
+                      post = link_id, text = body, r.depression = subreddit_id=="t5_2qqqf") %>%
+            filter(date < october10) %>%
+            group_by(author) %>%
+            arrange(date) %>%
+            mutate(time.last = c(NA, diff(date))/60/60/24) %>%
+            ungroup
+            
+user.post.data = 
+            transmute(user.post.data,
+                      author, subreddit_id, date = get.date(created_utc), type="post",
+                      post = name, text = paste(title, selftext), r.depression = subreddit_id=="t5_2qqqf") %>%
+            filter(date < october10) %>%
+            group_by(author) %>%
+            arrange(date) %>%
+            mutate(time.last = c(NA, diff(date))/60/60/24) %>%
+            ungroup
+
+user.data = 
+            rbind(user.post.data, user.comment.data)
+
+### Get phrases
+      source("Scripts/SI_Classification/ideation_phrases.R")
+      key.phrases = clean.text(key.phrases)
+      key.phrases = key.phrases[nchar(key.phrases) > 8]
+      key_phrase_regex = paste(key.phrases, collapse="|")
+
+### Classify text
+      user.data$txt = clean.text(user.data$text)
+      user.data$class = grepl(key_phrase_regex, user.data$txt, ignore.case = T)
+      user.data$txt = NULL
+
+      rm(list=setdiff(ls(), c("user.data","authors.noSI")))
+      
+save.image(file="Data/SI_Author_Sample/June_NoSI_Classified.RData")
+      
+      

### 2016-10-24 Scripts/5_Classify_SI_Author_Data.R

@@ -1,21 +1,0 @@
-load(file = "Data/June_Posts.RData")
-source("Suicide_Classification_Algorithms/ideation_phrases.R")
-
-### Get phrases
-      key.phrases = clean.text(key.phrases)
-      key.phrases = key.phrases[nchar(key.phrases) > 8]
-      key_phrase_regex = paste(key.phrases, collapse="|")
-
-### Classify text
-      comm.data$txt = clean.text(comm.data$body)
-      comm.data$class = grepl(key_phrase_regex, comm.data$txt, ignore.case = T)
-      comm.data$txt = NULL
-      
-      post.data$txt = clean.text(paste(post.data$title, post.data$selftext))
-      post.data$class = grepl(key_phrase_regex, post.data$txt, ignore.case = T)
-      post.data$txt = NULL
-      rm(list=setdiff(ls(), c("comm.data","post.data")))
-      
-save.image(file="Data/June_Posts_Classified.RData")
-      
-      

### 2016-10-24 Scripts/5_Combine_Authors.R

@@ -1,0 +1,57 @@
+
+### Create Dates
+      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
+      july1 = get.date("2016-07-01 00:00:00")
+      june1 = get.date("2016-06-01 00:00:00")
+      october10 = get.date("2016-10-10 16:00:00")
+      october1 = get.date("2016-10-01 00:00:00")
+      jan1 = get.date("2016-01-01 00:00:00")
+
+### Get Data
+      load(file="Data/SI_Author_Sample/June_SI_Classified.RData")
+      si.user.data = user.data
+      load(file="Data/SI_Author_Sample/June_NoSI_Classified.RData")
+      user.data = rbind(cbind(si.user.data, si.author=T), cbind(user.data, si.author=F))
+      rm(si.user.data)
+      rm(get.date)
+      
+### Load Packages
+      library(dplyr)
+      library(ggplot2)
+      options(width = 200)
+
+### Get rid of extra people
+      extras = with(user.data, 
+                    intersect(unique(author[si.author]), unique(author[!si.author])))
+      user.data = 
+            filter(user.data, !(author %in% extras & !si.author))
+      rm(extras)
+
+### Get rid of extra variables
+      user.data = select(user.data, author, date, type, r.depression, time.last, class,
+                         si.author)
+
+### Only take posts back to the first censor date of either posts or comments
+      user.data =
+            user.data %>%
+            group_by(author, type) %>%
+            mutate(oldest = min(date,na.rm=T),
+                   n = n()) %>%
+            ungroup() %>%
+            group_by(author) %>%
+            mutate(oldest = oldest[n == max(n)][1],
+                   n = max(n)) %>%
+            filter(n < 975 | date >= oldest) %>%
+            ungroup
+      
+### Summarize Author Data
+      author.summary =
+            user.data %>%
+            group_by(author, type) %>%
+            summarise(oldest = min(date),
+                      newest = max(date),
+                      si.author = any(si.author),
+                      n.post = n()) %>%
+            ungroup
+      
+save.image(file="Data/SI_Author_Sample/June_Authors_Combined.RData")

### 2016-10-24 Scripts/SI_Classification/ideation_phrases.R

@@ -11,7 +11,7 @@ clean.text <-function(x){
 }
 
 ### Read in the suicide lexicon
-words <- readLines("Scripts/2.2_SI_Classification/Suicide_Syntax.txt")
+words <- readLines("Scripts/SI_Classification/Suicide_Syntax.txt")
 words <- gsub("\t","",words)
 word.list <- list()
 category <- ""

### 2016-10-24 Paper_Rough_Draft.Rmd
Redo prosterior calculation with control group.

@@
 
-[give methods overview]
+Given that we cannot directly quantify the rate of suicide for online mental health boards, it is imperative that we develop a substitute to measure a similar construct.
+The construct that we propose is to estimate the total number of dropouts associated with suicidal ideation (SI).
 
@@
 ### Load Data
-      load(file = "Data/SI_Author_Sample/Author_Summary.RData")
-      user.summary = 
-            filter(user.summary, recent < 150) %>%
-            mutate(t = recent)
-      n = user.summary$n
-      eps = user.summary$eps
+      author.summary = 
+            user.data %>% 
+            group_by(author) %>%
+            summarise(n = n()-1,
+                      eps.bar = mean(time.last, na.rm=T),
+                      t = as.numeric(october10 - max(date)),
+                      si.author = si.author[1])
+            filter(author.summary, !t < 150)
+      n = author.summary$n
+      eps = author.summary$eps.bar
       eps[is.na(eps)] = 0 
-      t = user.summary$t
-      N = nrow(user.summary)
+      t = author.summary$t
+      N = nrow(author.summary)
+      si = author.summary$si.author
 ### Simulate Mu given Data
@@
       prior.p = 0.000001
-      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
-      post.E = colSums(apply(mu, 2, make.p, p=prior.p))/N * 100
-      hist(post.E, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
+      make.p = function(mu,p,t) p / (exp(-mu*t)*(1-p) + p)
+      post.si = colSums(apply(mu[si,], 2, make.p, p=prior.p, t=t[si]))
+      post.nosi = colSums(apply(mu[!si,], 2, make.p, p=prior.p, t=t[!si]))/sum(!si)*sum(si)
+      post.excess = post.si - post.nosi
+      hist(post.excess, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
            xlab="", ylab="")
-      ci = quantile(post.E, probs = c(0.025, 0.975))
+      ci = quantile(post.excess, probs = c(0.025, 0.975))
 ```
@@
 ### Calculate P(Q) from Mu and data
-      prior.p = c(0.5, 10^-(1:4))
-      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
-      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
-      user.summary2 = 
-            cbind(user.summary, post_p) %>%
-            select(-recent) %>%
-            melt(id.vars = c("author", "n", "eps", "t"),
-                 value.name = "post.p", variable.name = "prior.p")
-      ggplot(user.summary2) + 
-            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
-            facet_wrap("prior.p") + 
-            theme_bw() + 
-            xlab("Average Days between Posts") +
-            ylab("Days since Most Recent Post")
+      prior.p = 10^-seq(0.5,15.5, by=0.5)
+      post_p = sapply(prior.p, FUN = function(x){
+            post.si = colSums(apply(mu[si,], 2, make.p, p=x, t=t[si]))
+            post.nosi = colSums(apply(mu[!si,], 2, make.p, p=x, t=t[!si]))/sum(!si)*sum(si)
+            post.excess = post.si - post.nosi
+            return(quantile(post.excess, probs = c(0.025, 0.5, 0.975)))
+      })
+      colnames(post_p) = paste0("p10e-", seq(0.5,15.5, by=0.5))
+      post_p = cbind(Percentile = rownames(post_p), as.data.frame(post_p))
+      post_p = melt(post_p, id.vars = "Percentile", 
+                    variable.name = "Prior P",
+                    value.name = "Estimate")
+      ggplot(post_p)
+
 ```

### 2016-10-25 Paper_Rough_Draft.Rmd
Edited rough draft.

--- 2016-10-24 Paper_Rough_Draft.Rmd
@@
 ---
-title: "Do Reddit /r/depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates?"
+title: "Reddit /r/Depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates"
 author: "Lacey Etzkorn"
-date: "October 18, 2016"
+date: "October 24, 2016"
 output: 
@@
 options(digits = 4)
-load("June_Authors_Combined.RData")
+load("Data/SI_Author_Sample/June_Authors_Combined.RData")
 ```
@@
 Surrogate outcomes for suicide are currently in development.
-For example, Munmun de Choudhury uses [linguistic machine learning methods] to identify and predict user-specific shifts from discussing poor mental health to discussing suicide ideation.
+For example, Munmun de Choudhury uses [linguistic machine learning methods] to identify and predict user-specific shifts from discussing poor mental health to discussing suicide ideation [CITATION].
 However, detecting suicidal ideation in user posts has limited utility when the desired outcome is a rate of suicide.
 
-In this paper, we propose a more direct method for estimating rates of suicide from social media data.
-[Do we actually do this?] We do this by estimating the rate at which users who admit to having suicidal ideation (SI) stop posting on Reddit.
-We then compare the drop-out rates between SI-positive and SI-negative users.
+We propose an alternative parameter, similar in idea to a suicide rate, that community moderators could estimate with available data: the excess expected number of Reddit authors who abandon their accounts (drop out) after expressing suicidal ideation (SI).
+When we use the term "excess", we refer to the number of dropouts above what we would expect from an equal-sized comparable sample of authors who did not express suicidal ideation.
+This parameter is only defined for a population of authors who write in a given online community during a given time interval.
+For example, in this paper we define our population as the set of Reddit authors who post in /r/depression during the month of June 2016.
+We compare the number of dropouts from the authors who expressed suicidal ideation in June /r/depression (SI-postive authors), to a random sample of authors who did not express suicidal ideation in June /r/depression (SI-negative users).
+
 Though our method is thoroughly problematic in its current state, we believe that, with a proper amount of statistical development and validation, it has the potential to become a decent measure of suicide rates in online mental health communities.
@@
 
-[give methods overview]
+The objective of our project is to estimate the number of suicides for /r/depression authors who post in the month of June 2016.
+However, this objective is impossible given the available Reddit data.
+Since we cannot directly quantify the rate of suicide among online mental health boards, we propose an estimable surrogate parameter for a suicide rate: the excess expected number of drop-outs among SI-positive June /r/depression authors.
 
-The objective of our project is to quantify the risk of suicide for /r/depression authors. However, this objective is impossible for a number of reasons.
+The process of collecting the necessary data and estimating this parameter can be broken down into 4 modular steps:
 
-Another potential es
+* Collect all posts and comments from /r/depression in June 2016. (See data collection.)
 
-Given that the desired objective is impossible, we set out to estimate a reasonable surrogate parameter that will still be useful to online community moderators.
-Hence, we define the following parameter.
+* Classify whether each post or comment contained evidence of SI.
+Label authors as SI-positive if they had any posts or comments with SI in June 2016 /r/depression.
+Otherwise they are SI-negative.
+(See SI Classification.)
 
-The difference in rate of dropouts
+* Collect all available post and comment data for every SI-positive authors.
+Collect all available post and comment data for a similar-sized simple random sample of SI-negative authors.
+[Code Reference]
 
-The goal of our analysis is to estimate the difference in drop out rates between Reddit /r/depression authors who express suicidal ideation and /r/depression authors who don't
+* Estimate the number of drop-outs for each the SI-postitive and SI-negative groups.
+Subtract the latter estimate from the former to get an estimate of the number of excess dropouts among SI-positive authors.
+(See Estimation of Drop-Out Totals.)
 
-### Data
+* If a bayesian approach was used, examine the relationship between the estimate and the priors.
+
+### Data Collection
 
 Our target population is Reddit authors who post in the subreddit /r/depression in the month of June.
-Hence, we scrape all available (as of October 10, 2016) comment and post data from /r/depression for the month of June using the python package subredditarchive.
+Hence, we scrape all available (as of 4pm October 10, 2016) comment and post data from /r/depression for the month of June using the python package subredditarchive [cite].
 The month June was chosen to ensure that we have at least three months of follow-up time for each author.
 An earlier month wasn't chosen because Reddit censors author comment and post history to the most recent 1,000 items each.
-Henceforth we will refer to comments and posts collectively as posts.
 
-We then identified whether the text from each post contained evidence of suicidal ideation (SI) according to our classification algorithm.
-Details of this classification process are described in a subsequent section.
-Then, we produced one list of unique author ids associated with any SI evidence as well as one equal-sized list of unique authors without any SI evidence.
-We then scraped the post history for both lists of authors and identified posts with SI evidence.
+### Estimation of Drop-Out Totals
 
-### Estimation of Drop-Out Rates
-
-Our goal is to estimate the expected rate at which SI-positive and SI-negative authors stop using Reddit.
-Ultimately, we will compare our estimated rates between these two groups to determine if there is some association between suicidal ideation and risk of dropping-out.
+Our goal is to estimate the number of drop-outs for each SI-positive and SI-negative groups.
+Ultimately, we will compare our estimated drop-outs between these two groups to determine if there is some association between suicidal ideation and risk of dropping-out.
 
@@
 
-Our goal for our SI classification algorithm was to produce a set of comments that almost certainly contained only true SI comments.
-Hence, we set out to maximize specificity while throwing sensitivity out the window.
-While we recognize that could be many algorithms better suited for our final goal of estimating the incidence of suicide in our population, we were fine to just make something that worked for now.
+The goal for our classification algorithm is to determine whether comments and posts contain expressions of suicidal ideation.
+From these classifications, we produce a set of authors that express SI in June /r/Depression.
 
-[Definition of Suicidal Ideation]
+The CDC defines suicidal ideation, or thoughts about suicide, as "thoughts of engaging in suicide-related behavior" [cite] and "Thinking about, considering, or planning suicide." [cite].
+We broaden this definition for our analysis to the following:
 
-We began by reading through a sample of 100 randomly selected comments from various mental health subreddits to get a sense of how people expressed suicidal ideation on Reddit in general.
-From each of the SI comments from this 100, we extracted the smallest phrase(s) that contained evidence of SI.
-Examples of these phrase bits include:
+      Suicidal Ideation: Thinking about, considering, or planning suicide; desire to die; desire to stop living; or engagement in highly dangerous activities or self harm with the implicit goal of ending life.
+Suicidal ideation does not include hating or frustration with one's own life, extreme anguish or psychological distress, or engagement in highly dangerous activities or self harm where there is no implicit goal of ending one's life.
+
+It is important to note that we expected SI expression to be fairly rare among /r/Depression posts.
+Thus, in order to get a good estimate of the difference in drop-out rates between true SI-positive and true SI-negative authors, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors.
+However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive users to be so rare.
+In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.
+
+We read through a sample of 750 randomly selected comments and posts from June /r/Depression, and we classify SI according to the definition above.
+From each of the SI-positive comments, we extract the smallest phrase(s) that contained evidence of SI.
+Examples of these phrases include:
 
 * "I think about suicide"
+
 * "I just don't want to live""
+
 * "I have struggled with depression and suicidal thoughts"
+
 * "my suicide plan"
+
 * "I still feel like blowing my brains out"
 
-We then categoized these phrases into 12 linguistically distinct modes of expressing SI, adding extra where we felt appropriate:
+We then categoize collected phrases into twelve linguistically distinct modes of expressing SI.
+We discarded phrases that we felt were too linguistically complex for any classification algorithm to handle.
+The twelve modes are:
 
-Intention to, or thoughts of suicide/dying:
 * [I am] [intending to] [suicide verb]
+
 * [I am] [thinking about] [suicide noun]
+
 * I [intend to] [suicide verb]
+
 * I [suicide verb]
+
 * [I am] [suicide adjective]
+
 * Why not [suicide verb]
+
 * I [think about] [suicide noun]
-* I [think]
+
 * me [suicide verb]
+
 * me [suicide noun]
 
-Oppose life:
-* [I] [oppose] [live noun]
-* [I] [am opposed to] [living]
+* I [oppose] [live noun]
 
-For each of these modes of SI expression, we generated all possible combinations of words for each category to get all possible phrases for that mode.
-For example, to generate all possible phrases for  "I [intend to] [suicide verb]", we combined the "intend to" verbs
+* I [am opposed to] [living]
 
-      want to, were to, would like to, wish to, decided to, decide to, am not afraid to, am not scared to, have to, had to, try to, tried to, would like to, can, will, must, might, should, could, intend to, intended to, have come to, 've come to, ‘d like to, ‘d, ‘ll
-
-with the suicide verbs
+The phrases or words in brackets represent a broader class of phrases that could be inserted in it's place.
+For example, [suicide verb] could be replaced with any of the following phrases to still consitute evidence of SI expression:
 
@@
 
+For each of these modes of SI expression, we generate all possible combinations of phrases.
 After all phrases for all 12 modes of SI expression have been generated, we remove all punctuation and spacing from both the post text and the phrase text.
@@
 
-```{r , echo=FALSE, message=FALSE, warning=FALSE}
+```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=10}
 user.data = 
@@
 ### Now get overall credible interval for sum(Q)
-      prior.p = 0.000001
-      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
-      post.E = colSums(apply(mu, 2, make.p, p=prior.p))/N * 100
-      hist(post.E, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
+      prior.p = 10^-10
+      make.p = function(mu,p,t) p / (exp(-mu*t)*(1-p) + p)
+      post.si = colSums(apply(mu[si,], 2, make.p, p=prior.p, t=t[si]))
+      post.nosi = colSums(apply(mu[!si,], 2, make.p, p=prior.p, t=t[!si]))/sum(!si)*sum(si)
+      post.excess = post.si - post.nosi
+      hist(post.excess, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
            xlab="", ylab="")
-      ci = quantile(post.E, probs = c(0.025, 0.975))
+      ci = quantile(post.excess, probs = c(0.025, 0.975))
 ```
@@
 We found that our conclusions were highly sensitive to our specified prior probability of drop-outs.
+The plot below shows posterior credible intervals for the expected number of excess dropouts among authors who penned SI-positive posts in June /r/depression.
+
+If we set our prior probability of dropping out equal to 0.5, we would conclude that among the 491 authors who wrote SI-postitive posts in June /r/depression, there were only about 14 excess reddit drop-outs.
+However, when we set our prior probability of dropping out below $10^{-5}$, our estimates for excess dropouts associated with SI are in the range of 45 to 55.
 
@@
 ### Calculate P(Q) from Mu and data
-      prior.p = c(0.5, 10^-(1:4))
-      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
-      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
-      user.summary2 = 
-            cbind(user.summary, post_p) %>%
-            select(-recent) %>%
-            melt(id.vars = c("author", "n", "eps", "t"),
-                 value.name = "post.p", variable.name = "prior.p")
-      ggplot(user.summary2) + 
-            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
-            facet_wrap("prior.p") + 
-            theme_bw() + 
-            xlab("Average Days between Posts") +
-            ylab("Days since Most Recent Post")
+      prior.p = 10^-seq(0.5,15.5, by=0.5)
+      post_p = sapply(prior.p, FUN = function(x){
+            post.si = colSums(apply(mu[si,], 2, make.p, p=x, t=t[si]))
+            post.nosi = colSums(apply(mu[!si,], 2, make.p, p=x, t=t[!si]))/sum(!si)*sum(si)
+            post.excess = post.si - post.nosi
+            return(quantile(post.excess, probs = c(0.025, 0.5, 0.975)))
+      })
+      colnames(post_p) = paste0("p10e-", seq(0.5,15.5, by=0.5))
+      #post_p = cbind(Percentile = rownames(post_p), as.data.frame(post_p))
+      #post_p = melt(post_p, id.vars = "Percentile", 
+      #              variable.name = "Prior P",
+      #              value.name = "Estimate")
+      ggplot() +
+            geom_errorbar(aes(ymax = post_p[3,], ymin = post_p[1,], x=prior.p)) +
+            geom_point(aes(y= post_p[2,], x=prior.p)) + 
+            scale_x_log10() + 
+            xlab("Prior Probability of Quitting Reddit") + 
+            ylab("Excess Droup-Outs Associated with SI") +
+            ggtitle("Posterior Credible Intervals for Total SI-Associated Drop-Outs") 
 ```
+
+Given the discrepancy in conclusions we would draw between a large prior and small prior, we reccomend that a small prior be used for the following reason: large prior probabilities of dropping out inflate author-specific posterior probabilities of dropping out with artificial evidence.
+If instead we use a small prior-probability of dropping out, our posterior estimate that a given author has dropped out relies more heavily on their data: whether the time since an author's most recent post is unusually high compared to their post history.
+Hence, the estimates of total number of drop-outs among SI-postitive and SI-negative authors respectively is (1) more conservative and (2) requires more data-based evidence.
+Consequently, the difference in estimated drop-out rates between SI-positive and SI-negative authors is driven more by the data and less by the prior.
+
+In our previous results, we present a credible interval derived from a prior of $10^-5$ for this reason.
+The interpretation of this prior is as follows: without seeing any data, we would expect about 0.01 of our approximate 1,000 authors to drop out of reddit.
 
@@
 
+We only estimate the proposed parameter for one month of data. We do not propose a framework for extending this estimation longitudionally.
+
+Do we continue to follow users from June to see if they post more often and adjust their drop-out probabilities accordingly?
+
+Why did we choose three months? We could have chosen a shorter or longer interval. If the interval gets longer, our estimates should become more and more accurate...
+
+The times between posts are more likely a mixture of exponentials rather than just one exponential...
+
+This method should be examined jointly with a number of other month-to-month characteristics of online communities such as the total number of authors, the total number of authors that express suicidal ideation, etc.
+
+How to deal with people who post comments with suicidal ideation over time?
+
 # Works Cited
@@
 * Social Media Embraces Suicide Prevention CMAJ August 11, 2015 vol. 187 no. 11 First published June 29, 2015, doi: 10.1503/cmaj.109-5104 http://www.cmaj.ca/content/187/11/E333.short
+
+* http://www.cdc.gov/violenceprevention/suicide/definitions.html
+
+* https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2576496/
+
+http://www.cdc.gov/violenceprevention/suicide/definitions.html

### 2016-10-27 Paper_Rough_Draft.Rmd
edited rough draft. added supplement.

@@
 ```
+
+Collaborators: Linda Gai
+
+Peer Editors: Guanghao Qi, Matt Cole
+
+Supplemental Materials: [Supplement](Supplement.html).
 
@@
 
-The goal for our classification algorithm is to determine whether comments and posts contain expressions of suicidal ideation.
+##### SI Definition
+
+The goal for our classification algorithm is to determine whether comments and posts contain expressions of suicidal ideation (SI).
 From these classifications, we produce a set of authors that express SI in June /r/Depression.
@@
 The CDC defines suicidal ideation, or thoughts about suicide, as "thoughts of engaging in suicide-related behavior" [cite] and "Thinking about, considering, or planning suicide." [cite].
-We broaden this definition for our analysis to the following:
+For our analysis, we change this definition to the following:
 
-      Suicidal Ideation: Thinking about, considering, or planning suicide; desire to die; desire to stop living; or engagement in highly dangerous activities or self harm with the implicit goal of ending life.
-Suicidal ideation does not include hating or frustration with one's own life, extreme anguish or psychological distress, or engagement in highly dangerous activities or self harm where there is no implicit goal of ending one's life.
+We define suicidal ideation (SI) as thinking about, considering, or planning suicide; desire to die; desire to stop living; or engagement in highly dangerous activities or self harm with the implicit goal of ending life.
+It may include admissions of having suicidal ideation in the past or the potential for suicidal ideation in the future.
+Evidence of suicidal ideation does not follow from hating or frustration with one's own life, extreme anguish or psychological distress, or engagement in highly dangerous activities or self harm where there is no implicit goal of ending one's life.
+However, explicit statements about wanting to die or engage in suicide are taken literally.
 
-It is important to note that we expected SI expression to be fairly rare among /r/Depression posts.
-Thus, in order to get a good estimate of the difference in drop-out rates between true SI-positive and true SI-negative authors, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors.
-However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive users to be so rare.
+We change our definition of suicidal ideation to make it clearer what kinds of Reddit comments may constitute SI.
+For example, the phrase "I don't want to live." does not fall under the CDC SI definition since there is no explicit thoughts of lethal self-harm.
+Rather, this statement expresses SI through a double-negative.
+While this definition does not fit a traditional definition of SI, we include these kinds of comments because Reddit moderators may be equally worried about authors who express these comments.
+
+##### The Algorithm
+
+A number of methods have been implemented to detect suicidal ideation from user-generated text on social media [CITE]. However, for simplicity, we do not use them here.
+
+We expected SI expression to be fairly rare among /r/Depression posts.
+Thus, in order to get a good estimate of the drop-out risk attributable to SI, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors.
+However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive author to be so rare, and hence not have much influence on our estimate of the SI-negative drop-out risk.
 In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.
 
-We read through a sample of 750 randomly selected comments and posts from June /r/Depression, and we classify SI according to the definition above.
-From each of the SI-positive comments, we extract the smallest phrase(s) that contained evidence of SI.
-Examples of these phrases include:
+With an intent to achieve this goal, we design an algorithm that searches post text for at least one phrase from an explicit list of SI-expressive phrases that constitute strong evidence of suicidal ideation [Supplement Reference].
 
-* "I think about suicide"
-
-* "I just don't want to live""
-
-* "I have struggled with depression and suicidal thoughts"
-
-* "my suicide plan"
-
-* "I still feel like blowing my brains out"
-
-We then categoize collected phrases into twelve linguistically distinct modes of expressing SI.
-We discarded phrases that we felt were too linguistically complex for any classification algorithm to handle.
-The twelve modes are:
-
-* [I am] [intending to] [suicide verb]
-
-* [I am] [thinking about] [suicide noun]
-
-* I [intend to] [suicide verb]
-
-* I [suicide verb]
-
-* [I am] [suicide adjective]
-
-* Why not [suicide verb]
-
-* I [think about] [suicide noun]
-
-* me [suicide verb]
-
-* me [suicide noun]
-
-* I [oppose] [live noun]
-
-* I [am opposed to] [living]
-
-The phrases or words in brackets represent a broader class of phrases that could be inserted in it's place.
-For example, [suicide verb] could be replaced with any of the following phrases to still consitute evidence of SI expression:
+These phrases were derived from a random sample of 750 June 2016 /r/Depression comments.
+Human classifiers read through each comment, labeled whether it contained SI expression, and recorded the smallest phrase(s) from that comment that the classifier felt constituted evidence of SI.
+We then organized the phrases into twelve categories, and noted in brackets where words could be exchangable.
+For example, [suicide verb] could be replaced with any of the following phrases to still consitute evidence of SI:
 
@@
 
-For each of these modes of SI expression, we generate all possible combinations of phrases.
-After all phrases for all 12 modes of SI expression have been generated, we remove all punctuation and spacing from both the post text and the phrase text.
-We combine all phrases into a regular expression using the or "|" operator, and then use the function "grepl" to test whether each post contains any phrase.
-
 # Results
 
-### June /r/depression
+### June /r/Depression
 
-For the month of June, /r/depression contained 22,041 posts, representing contributions from 7,572 authors. We identified 547 SI-positive posts from 492 unique users.
-
-In a sample of 100 SI-positive posts, [n] did not have true SI evidence. In a sample of 100 SI-negative posts, [n] did have SI evidence.
+For the month of June, /r/depression contained 22,041 posts, representing contributions from 7,572 authors.
+We identified 547 SI-positive posts from 492 unique authors.
+In a simple random sample of 100 SI-positive posts, 12 did not have true SI evidence.
+In a simple random sample of 100 SI-negative posts, 4 did have true SI evidence.
 
@@
 ```
-
-After scraping the post history for each of the SI-positive users, we find no post or comment data for 1 author, and we find 16 authors whose full history was not available back to April 2016.
-We are left with 475 authors.
-
-The post histories for our 475 authors are depicted above.
+**Figure 1:** *Post histories for SI-Positive authors and SI-Negative authors are different.* 
+The post histories for our authors are depicted above.
 Each y value represents a unique author id, sorted by the time of their most recent post.
@@
 Grey posts represent posts elsewhere on Reddit.
+
 There a number of important features in this plot.
@@
 ```{r, echo=FALSE, warning=FALSE}
-### Load Data
-      author.summary = 
-            user.data %>% 
-            group_by(author) %>%
-            summarise(n = n()-1,
-                      eps.bar = mean(time.last, na.rm=T),
-                      t = as.numeric(october10 - max(date)),
-                      si.author = si.author[1])
-            filter(author.summary, !t < 150)
-      n = author.summary$n
-      eps = author.summary$eps.bar
-      eps[is.na(eps)] = 0 
-      t = author.summary$t
-      N = nrow(author.summary)
-      si = author.summary$si.author
-### Simulate Mu given Data
-      alpha = 1; beta = 1
-      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
-### Now get overall credible interval for sum(Q)
-      prior.p = 10^-10
-      make.p = function(mu,p,t) p / (exp(-mu*t)*(1-p) + p)
-      post.si = colSums(apply(mu[si,], 2, make.p, p=prior.p, t=t[si]))
-      post.nosi = colSums(apply(mu[!si,], 2, make.p, p=prior.p, t=t[!si]))/sum(!si)*sum(si)
-      post.excess = post.si - post.nosi
-      hist(post.excess, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
+load("Data/Posteriors/Attributable_10e-10.Rdata")
+hist(post.excess, 
+     main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
      xlab="", ylab="")
@@
 
-We found that our conclusions were highly sensitive to our specified prior probability of drop-outs.
+We found that our conclusions were sensitive to our specified prior probability of drop-outs.
 The plot below shows posterior credible intervals for the expected number of excess dropouts among authors who penned SI-positive posts in June /r/depression.
@@
 ```{r, echo=FALSE, warning=FALSE}
-### Calculate P(Q) from Mu and data
-      prior.p = 10^-seq(0.5,15.5, by=0.5)
-      post_p = sapply(prior.p, FUN = function(x){
-            post.si = colSums(apply(mu[si,], 2, make.p, p=x, t=t[si]))
-            post.nosi = colSums(apply(mu[!si,], 2, make.p, p=x, t=t[!si]))/sum(!si)*sum(si)
-            post.excess = post.si - post.nosi
-            return(quantile(post.excess, probs = c(0.025, 0.5, 0.975)))
-      })
-      colnames(post_p) = paste0("p10e-", seq(0.5,15.5, by=0.5))
-      #post_p = cbind(Percentile = rownames(post_p), as.data.frame(post_p))
-      #post_p = melt(post_p, id.vars = "Percentile", 
-      #              variable.name = "Prior P",
-      #              value.name = "Estimate")
+      load("Data/Posteriors/Attributable_All.Rdata")
+      load("Data/Posteriors/Priors_All.Rdata")
       ggplot() +

### 2016-10-27 Supplement.Rmd
edited rough draft. added supplement.

---
title: "Supplemental Details"
author: "Lacey Etzkorn"
date: "October 26, 2016"
output: 
      html_document:
            toc: TRUE
---

# Data Collection

The goal of our analysis is to estimate the expected number of drop-outs attributable to SI among June /r/Depression authors. The process of collecting the necessary data and estimating this parameter can be broken down into 4 modular steps:

1. **Collect all posts and comments from /r/depression in June 2016. **
We use the package subredditarchive, and modify the existing code from the python script here: https://github.com/peoplma/subredditarchive. The modified code that we used to scrape the June data can be found in 
[Scripts/0_Scrape_June_Data.py](Scripts/0_Scrape_June_Data.py).
Parse the json files for each thread for the main post and comments. For each, grab information on author, title (if applicable), text, creation date, name/link id, etc. 
(See code: [Scripts/1_Read_Json_Files.R](Scripts/1_Read_Json_Files.R))

2. **Combine and Classify June.**
Combine post and comment data into one data frame where the level of each observation is either a post or comment. Classify whether each post or comment from contained evidence of SI. (See [SI Classification](#si-classification)). 
Label authors as SI-positive if they had any posts or comments with SI in June 2016 /r/depression. Otherwise they are SI-negative. List unique SI-positive authors.
(See code: [Scripts/2_Combine_Classify_June_Posts_Comments.R](Scripts/2_Combine_Classify_June_Posts_Comments.R))

3. **Scrape Author Data.**
Collect all available post and comment data for every SI-positive authors. Collect all available post and comment data for a similar-sized simple random sample of SI-negative authors. We collected ours at 4pm on October 10, 2016.
(See code: [Scripts/3.1_Scrape_User_Data.R](Scripts/3.1_Scrape_User_Data.R) and
[Scripts/3.2_Scrape_NoSI_User_Data.R](Scripts/3.2_Scrape_NoSI_User_Data.R))

4. **Drop-Out Estimation.** Estimate the expected number of drop-outs attributable to SI. 
(See derivation: [Estimation of Drop-Out Totals](#estimation-of-drop-out-totals), 
see code: [Scripts/6_MC_Estimation.R](Scripts/6_MC_Estimation.R))

5. If a bayesian approach was used, examine the relationship between the estimate and the priors.

# Estimation of Drop-Out Totals

Derivation:

Let $i$ index the authors. Let $Q_i$ be the (unobserved) event that author $i$ has quit Reddit. Let $t_i$ be the time since observing the most recent post from author $i$. Let $y_i$ be the (unobserved) length of time from the most recent post to the next post in the future. If author $i$ has quit Reddit, then $y_i = \infty$. Let $n_i$ be the observed number of intervals between posts for author $i$. Let $\bar{\epsilon_i}$ be the observed average time between Reddit posts for author $i$. Let $SI_i$ be the (unobserved) indicator that author $i$ dropped off of Reddit. Let $\rho$ be the prior probability (which we define) that any author drops out of Reddit.

Our goal is to do monte-carlo sampling from the posterior distribution of 
$E(\sum_i Q_i | SI_i=1) - E(\sum_i Q_i | SI_i=0)$.

First assume that the post histories of each author are a Poisson process, and so observed times between posts are exponentially distributed with parameter $\lambda_i$. For each $\lambda_i$, specify the prior distribution $\lambda_i \sim gamma(1,1)$. 
Hence the posterior for $\lambda_i$ is 
$\lambda_i \big |n_i,\bar{\epsilon_i} \sim gamma(n_i + 1, 1 + n_i\cdot\bar{\epsilon_i})$. [CITE RESULT].

Given $\lambda_i$ and prior $\rho$, we are able to calculate the probability that the author has stopped using Reddit using Bayes Rule.
$$ P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)
            =  \frac{P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) \cdot \rho}
                        {P(y_i > t_i|\lambda_i, t_i, \rho)}
            =   \frac{\rho} {e^{-\lambda_i\cdot t_i} \cdot (1-\rho) + \rho} 
$$ 
Note that $P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) = 1$ since $y_i = \infty$ for the event $Q_i$. Also note that marginal to $Q_i$, $y_i$ follows a mixture of infinity with probability $\rho$ and an exponential with parameter $\lambda_i$ and probability $\rho$.

Now, if we consider each $Q_i$ to be independent, and we are given $P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$ for each author, then 
$$E(\sum_i Q_i| SI_i = 1) - E(\sum_i Q_i| SI_i = 0) = 
      \sum_i (-1)^{SI_i +1} P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$$

Hence, using these formulas, we can generate monte-carlo samples from the posterior distribution for the expected number of drop-outs attributable to SI.

# SI Classification

Phrase Recipes:

* [I am] [intending to] [suicide verb]

* [I am] [thinking about] [suicide noun]

* I [intend to] [suicide verb]

* I [suicide verb]

* [I am] [suicide adjective]

* Why not [suicide verb]

* I [think about] [suicide noun]

* me [suicide verb]

* me [suicide noun]

* I [oppose] [live noun]

* I [am opposed to] [living]

### 2016-10-27 Scripts/6_MCMC.R

@@ -1,40 +1,0 @@
-
-### Load Data
-      load(file = "Data/SI_Author_Sample/Author_Summary.RData")
-      library(ggplot2)
-      library(reshape2)
-      user.summary = 
-            filter(user.summary, recent < 150) %>%
-            mutate(t = recent)
-      n = user.summary$n
-      eps = user.summary$eps
-      eps[is.na(eps)] = 0 
-      t = user.summary$t
-      N = nrow(user.summary)
-      
-### Simulate Mu given Data
-      alpha = 1; beta = 1
-      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
-      dim(mu)
-
-### Calculate P(Q) from Mu and data
-      prior.p = c(0.5, 10^-(1:4))
-      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
-      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
-      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
-      user.summary2 = 
-            cbind(user.summary, post_p) %>%
-            select(-recent) %>%
-            melt(id.vars = c("author", "n", "eps", "t"),
-                 value.name = "post.p", variable.name = "prior.p")
-      ggplot(user.summary2) + 
-            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
-            facet_wrap("prior.p") + 
-            theme_bw()
-
-### Now get overall credible interval for sum(Q)
-      prior.p = 0.000001
-      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
-      post.E = colSums(apply(mu, 2, make.p, p=prior.p))
-      hist(post.E, main = "Posterior Distribution for \n Expected Total Reddit Drop-Outs")
-      

### 2016-10-27 Scripts/6_MC_Estimation.R

@@ -1,0 +1,56 @@
+### Load Data
+      load("Data/SI_Author_Sample/June_Authors_Combined.RData")
+      require(dplyr)
+
+### Summarize to Author Level
+      author.summary = 
+            user.data %>% 
+            group_by(author) %>%
+            summarise(n = n()-1,
+                      eps.bar = mean(time.last, na.rm=T),
+                      t = as.numeric(october10 - max(date)),
+                      si.author = si.author[1]) %>%
+            filter(t < 150)
+      n = author.summary$n
+      eps = author.summary$eps.bar
+      eps[is.na(eps)] = 0 
+      t = author.summary$t
+      N = nrow(author.summary)
+      si = author.summary$si.author
+### Simulate Mu given Data
+      mu = replicate(n = 10000, rgamma(N, shape = 1 + n, rate = 1 + n*eps))
+### Now get overall credible interval for sum(Q)
+      prior.p = 10^-10
+      post.si = 
+            apply(mu[si,], 2, 
+                  function(mu,p,t) p / (exp(-mu*t)*(1-p) + p), 
+                  p=prior.p, 
+                  t=t[si]) %>%
+            colSums
+      post.nosi = 
+            apply(mu[!si,], 2, 
+                  function(mu,p,t) p / (exp(-mu*t)*(1-p) + p), 
+                  p=prior.p, 
+                  t=t[!si]) %>%
+            colSums
+      post.excess = post.si - post.nosi
+      
+### Save Posterior Samples
+      save(post.excess, file = "Data/Posteriors/Attributable_10e-10.Rdata")
+
+### Calculate P(Q) from Mu and data
+      prior.p = 10^-seq(0.5,15.5, by=0.5)
+      get.p = function(mu,p,t) p / (exp(-mu*t)*(1-p) + p)
+      post_p = 
+            sapply(prior.p, FUN = function(x){
+                  post.si = colSums(apply(mu[si,], 2, get.p, p=x, t=t[si]))
+                  post.nosi = colSums(apply(mu[!si,], 2, get.p, p=x, t=t[!si]))/sum(!si)*sum(si)
+                  post.excess = post.si - post.nosi
+                  return(quantile(post.excess, probs = c(0.025, 0.5, 0.975)))
+            })
+      colnames(post_p) = paste0("p10e-", seq(0.5,15.5, by=0.5))
+
+### Save Posterior Samples
[…]

### 2016-10-27 Scripts/SI_Classification/Assign_Test_Values.R

@@ -1,13 +1,27 @@
-load(file="Data/Training_Lacey2.RData")
+load(file="Data/June_Depression_Sample/June_Posts_Classified.RData")
+require(dplyr)
 
-for(i in 1:nrow(lacey2)){
-      writeLines(paste(lacey2[i,"title"],"\n",
-          lacey2[i,"post.text"], "\n",
-          lacey2[i,"suicidal"]))
-      lacey2$suicidal[i] <- readline(prompt="Current Suicide Ideation (0,1):") 
+### Sample 100 of each SI-positive and SI-negative
+      si.positive.sample = 
+            filter(user.data, si) %>%
+            sample_n(100)
+      
+      si.negative.sample =
+            filter(user.data, !si) %>%
+            sample_n(100)
+      
+      test.sample = rbind(si.negative.sample, si.positive.sample)
+
+rm(user.data, si.positive.sample, si.negative.sample)
+
+for(i in 1:nrow(test.sample)){
+      cat(test.sample[i,"text"], "\n")
+      test.sample$suicidal[i] <- readline(prompt="Current Suicide Ideation (0,1):") 
+      test.sample$phrase[i] <- readline(prompt="SI evidence:") 
 }
 
-save(lacey2, file="Data/Training_Lacey2_Classified.RData")
+test.sample$suicidal[!test.sample$phrase ==""] <- 1
+test.sample$suicidal[test.sample$suicidal ==""] <- 0
+test.sample$suicidal[!test.sample$suicidal %in% c("0","1")] <- test.sample$phrase[!test.sample$suicidal %in% c("0","1")] 
 
-table(lacey2$suicidal)
-
+save(test.sample, file="Data/Test/Test_Classified.Rdata")

### 2016-10-28 Paper_Rough_Draft.Rmd
edited rough draft. added figure descriptions

@@
 We identified 547 SI-positive posts from 492 unique authors.
-In a simple random sample of 100 SI-positive posts, 12 did not have true SI evidence.
-In a simple random sample of 100 SI-negative posts, 4 did have true SI evidence.
+In a simple random sample of 100 SI-positive posts, and 100 SI-positive posts, we estimated the positive predictive value to be 88% (80%, 94%) and the negative predictive value to be 96% (90%, 99%).
 
@@
 
-```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=10}
+```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=13, fig.height=6}
 user.data = 
@@
       ifelse(user.data$r.depression, "/r/depression","other")) %>%
-      ordered(labels = c("other", "/r/depression", "SI"))
+      ordered(labels = c("Other Subreddit", "/r/Depression", "SI Expressive"))
 user.data$si.group = 
@@
                size=point.label)) + 
-ggtitle("Distribution of Post Dates across Authors\nbetween Jan. and Oct.") +
+ggtitle("Distribution of Post Dates across Authors between Jan. and Oct.") +
 ylab("Author Rank by Newest Post") + xlab("Date") +
-geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.3) + 
-geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.3) + 
-scale_colour_manual(values = c("grey","darkblue", "red")) + 
-scale_size_manual(values = c(0.1,0.1,0.3)) + 
-scale_alpha_manual(values = c(0.1,0.1,1)) + 
-theme_bw() + facet_wrap("si.group")
+geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.5) + 
+geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.5) + 
+scale_colour_manual(name = "Post\nCharacteristics",
+                    values = c("grey","darkblue", "red")) + 
+scale_size_manual(name = "Post\nCharacteristics",
+                  values = c(0.1,0.1,0.3)) + 
+scale_alpha_manual(name = "Post\nCharacteristics",
+                   values = c(0.1,0.1,1)) + 
+theme_bw(20) + 
+theme(legend.key = element_blank(),
+      legend.position=c(1,0),
+      legend.justification = c(1,0),
+      legend.background = element_rect(fill=alpha('grey', 0)))+
+facet_wrap("si.group") +
+guides(color = guide_legend(override.aes = list(size=5, alpha = 1)))
+
 ```
-**Figure 1:** *Post histories for SI-Positive authors and SI-Negative authors are different.* 
-The post histories for our authors are depicted above.
-Each y value represents a unique author id, sorted by the time of their most recent post.
-Each x value represents the date of a post.
-Hence, we can read each horizontal line on this plot as the post history of one author.
-Red points represent SI-positive posts.
-Blue points represent posts in the /r/depression subreddit.
-Grey posts represent posts elsewhere on Reddit.
 
-There a number of important features in this plot.
+**Figure 1: Post histories for SI-Positive authors and SI-Negative authors are different.** Author ids are sorted along the y axis by time of the most recent post.
+Dates of posts are sorted along the x axis.
+Each horizontal strip of points represents a user history.
+Posts are red if they contain SI expression, regardless of their subreddit.
+Posts without SI expression are blue if they are in the subreddit /r/Depression, or they are otherwise grey.
+Vertical grey lines outline the month of June, from which data was sampled.
+
+Figure 1 reveals a number of characteristics about the authors in our study.
 First, we note that those authors who posted more recently tended to post more often, which is expected.
-Second we see that many authors made multiple SI-positive posts.
-Third, we see that nearly 170 of our 475 authors had their last post in June, which was the period that we used to sample from.
+Second we see that many authors made multiple SI-positive posts, even among the group that was SI-negative in June /r/depression.
+
+Figure 1 also illuminates a number of important differences between the SI-positive and SI-negative groups.
+The figure shows that nearly 170 of our 491 authors had their last post in June, which was the period that we used to sample from.
+In comparison, only about 100 of the SI-negative authors had their last post in June.
 Fourth, of these 170 authors, many did not post frequently before dropping-off Reddit.
-However, a hand-full of them had posted frequently, and their drop-put is therefore suspicious.
 
@@
 
-The histogram below represents the posterior distribution for the rate of drop-outs for authors whose June /r/depression comments were SI-positive.
-
-```{r, echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=5}
 load("Data/Posteriors/Attributable_10e-10.Rdata")
-hist(post.excess, 
-     main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
-     xlab="", ylab="")
 ci = quantile(post.excess, probs = c(0.025, 0.975))
@@
 
-Our 95% credible interval is (`r ci`), meaning there is a 95% probability that the expected rate of drop-out is between `r ci[1]` and `r ci[2]`.
+The histogram below represents the posterior distribution for the rate of drop-outs for authors whose June /r/depression comments were SI-positive.
+Our 95% credible interval is (`r ci`). Hence, there is a 95% probability that the expected SI-attributable drop-outs for authors in June 2016 /r/Depression is between `r ci[1]` and `r ci[2]`.
+
+```{r, echo=FALSE, warning=FALSE, message=F,fig.height=4, fig.width=5}
+ggplot() +
+geom_histogram(aes(x=post.excess),  
+               color="black", fill="blue", alpha=0.7) +
+ggtitle("Posterior Distribution for\nSI-Attributable Drop-Outs (Prior = 10e-4)")+
+xlab("Expected Number of SI-Attributable Drop-Outs") + 
+ylab("Count") + 
+theme_bw(12)
+```
+
+**Figure 2: 10,000 Posterior Monte-Carlo Samples for the Expected Number of SI-Attributable Drop-Outs.**
 
@@
 
-We found that our conclusions were sensitive to our specified prior probability of drop-outs.
-The plot below shows posterior credible intervals for the expected number of excess dropouts among authors who penned SI-positive posts in June /r/depression.
+We found that our conclusions were sensitive to our specified prior probability that any author dropped out.
+The plot below shows posterior credible intervals for the expected number of SI-attributable drop-outs in June /r/depression.
 
-If we set our prior probability of dropping out equal to 0.5, we would conclude that among the 491 authors who wrote SI-postitive posts in June /r/depression, there were only about 14 excess reddit drop-outs.
+If we set our prior probability of dropping out equal to 0.5, we would conclude that among the 491 authors who wrote SI-postitive posts in June /r/Depression, there were only about 14 excess reddit drop-outs.
 However, when we set our prior probability of dropping out below $10^{-5}$, our estimates for excess dropouts associated with SI are in the range of 45 to 55.
@@
 load("Data/Posteriors/Priors_All.Rdata")
+library(scales)
 ggplot() +
@@
 geom_point(aes(y= post_p[2,], x=prior.p)) + 
-            scale_x_log10() + 
+scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
+              labels = trans_format("log10", math_format(10^.x))) + 
+theme_bw(16) + 
 xlab("Prior Probability of Quitting Reddit") + 
-            ylab("Excess Droup-Outs Associated with SI") +
-            ggtitle("Posterior Credible Intervals for Total SI-Associated Drop-Outs") 
+ylab("Expected SI-Attributable Drop-Outs") +
+ggtitle("Posterior Credible Intervals for\nTotal SI-Attributable Drop-Outs") 
 ```
+
+**Figure 3: Posterior credible intervals for SI-attributable drop-outs across many priors.** Each point represents a posterior median for SI-attributable drop outs, while bars represent 2.5% and 97.5% quantiles.
+Prior probabilities of dropping out range from $\rho = 0.5$ to $\rho=10^{-15.5}$
 
@@
 
-### Limitations
+### Future Work
 
-For this method, we only incorporate user specific information as the time between posts.
-However, a number of other factors might give us information about whether a user actually attempts suicide.
-Sentiment might matter.
-Recent SI posts might matter.
-Actual suicide notes might matter.
+We list a number of extensions and adjustments for this project in order of priority.
 
-We do not differentiate between suicidal ideation and suicide notes.
+First, we need to adjust our estimates to account for the error in our SI classification algorithm.
+(See [June \r\Depression](#june-/r/depression).) Not knowing whether each author truly expressed SI in their text data should inflate the uncertainty of the estimate.
 
-We also cannot observe unsuccessful suicide attempts.
+Second, we need to propose a framework for extending our estimation longitudionally.
+Community moderators will want to measure SI-attributable drop-outs before and after interventions.
+However, it is not yet clear how we will measure SI-attributable drop-outs over time, especially when so many authors repeatedly express SI.
+In this paper, we only estimate the SI-attributable drop-outs for June 2016 authors with data collected at a single time point (October 10, 2016).
 
-We only estimate the proposed parameter for one month of data. We do not propose a framework for extending this estimation longitudionally.
+Third, our method does not properly account for counfounding relationships between SI and droping out.
+For example, moderators ban authors for "trolling." If being banned for trolling is more prevalent among SI-negative (or SI-positive) authors, our estimate of the drop-outs attributable to SI will be biased downward (or upward).
 
-Do we continue to follow users from June to see if they post more often and adjust their drop-out probabilities accordingly?
+Fourth, we need to better assess the fit of our model to the observed data.
+We use a parametric Bayesian approach to estimate each author's individual probability of having dropped out.
+In this framework, we assumed that times between an author's posts follow an exponential distribution.
+However, mixture of exponential distributions with adjustments for temporal trends may better fit the data.
 
-Why did we choose three months? We could have chosen a shorter or longer interval. If the interval gets longer, our estimates should become more and more accurate...
-
-The times between posts are more likely a mixture of exponentials rather than just one exponential...
-
-This method should be examined jointly with a number of other month-to-month characteristics of online communities such as the total number of authors, the total number of authors that express suicidal ideation, etc.
-
-How to deal with people who post comments with suicidal ideation over time?
+Fifth, we ignore the information the author's text may contain about dropping out or attempting suicide.
+For example, we do not differentiate between suicidal ideation and suicide plans.
+A body of psychological literature documents the importance of accounting for and quantifying suicidal intent and planning when examining suicide risk [CITE].
+However, attempting to mine such psychological measures from a large amount of text data is far beyond the scope of this paper and easily beyond the frontiers of psychological science and machine learning.
 

### 2016-10-29 Paper.Rmd
clean house

---
title: "Reddit /r/Depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates: An Attempt to Estimate Suicide Rates in a Data Void"
author: "Lacey Etzkorn"
date: "October 24, 2016"
output: 
      html_document:
            toc: TRUE
---

```{r setup, include=FALSE}
require(ggplot2); require(dplyr); require(reshape2)
options(width = 90)
options(digits = 4)
load("Data/SI_Author_Sample/June_Authors_Combined.RData")
```

Collaborators: Linda Gai

Peer Editors: Guanghao Qi

Supplemental Materials: [Supplement](Supplement.html).

# Introduction

The problem of suicide plagues social media and online communities devoted to mental health. 
Sadly, people who intend to commit suicide will often post last notes on sites such as Facebook, Twitter, and Reddit.
Additionally, health professionals often worry that unmonitored online interactions between individuals with mental illness could lead to exacerbation of symptoms and suicide clusters.

In response, social media has assumed a more active role in monitoring and protecting the mental health of its users. Facebook currently has a report form for users who see suicidal content in friend posts. Twitter took an even more active approach in 2014 when they partnered with the charity Samaritans to release an app that automatically detected tweets indicating emotional distress, and notified the user's contacts that the user might need help. However, the app was discontinued shortly due to privacy concerns.

Given the delicate relationship between social media and suicide, it is of utmost importance that community moderators study the impacts of their policies on their community's rate of suicide. However, community moderators do not have inferential tools to do so. This is due, in part, to the lack of data available to moderators. It is near impossible for moderators to observe actual outcomes of suicide, especially when users are anonymous.

We propose an alternative parameter, similar in idea to a suicide rate, that community moderators could estimate with available data: the expected number of Reddit authors who abandon their accounts (drop out) after expressing suicidal ideation (SI). More concisely, we can call this parameter the expected SI-attributable drop outs. When we use the term "excess", we refer to the number of dropouts above what we would expect from an equal-sized comparable sample of authors who did not express suicidal ideation. This parameter is only defined for a population of authors who write in a given online community during a given time interval. For example, in this paper we define our population as the set of Reddit authors who post in /r/Depression during the month of June 2016. We compare the drop outs from the authors who expressed suicidal ideation in June /r/Depression (SI-postive authors), to a random sample of authors who did not express suicidal ideation in June /r/Depression (SI-negative authors).

# Methods

The objective of our project is to estimate our parameter from Reddit data. Specifically, we will estimate the expected number drop-outs among authors who were identified as SI-positive in posts from June on /r/Depression.

The process of collecting the necessary data and estimating this parameter can be broken down into 4 modular steps. 
First we scrape all posts and comments from /r/Depression in June 2016. The month June was chosen to ensure that we have at least three months of follow-up time for each author. An earlier month wasn't chosen because Reddit censors author comment and post history to the most recent 1,000 items each. 
(See [Supplement/Data Collection](Supplement.html).) 
Second, we classify whether each post or comment express SI. We label authors as SI-positive if they had any posts or comments with SI in June 2016 /r/Depression. Otherwise they are SI-negative. (See [SI Classification](#si) for details.)
Third, we collect all available post and comment data for every SI-positive author and a similar-sized random sample of SI-negative authors from June /r/Depression. [Code Reference]
Fourth, we use Monte-Carlo sampling to get a posterior distribution for the expected SI-attributable drop outs. (See [Estimation of Drop Outs](#estimation-of-drop-outs).)

### SI Definition

The goal for our classification algorithm is to determine whether comments and posts contain expressions of suicidal ideation (SI). From these classifications, we produce a set of authors that express SI in June /r/Depression.

The CDC defines suicidal ideation, or thoughts about suicide, as "thoughts of engaging in suicide-related behavior" and "Thinking about, considering, or planning suicide" [2]. For our analysis, we change this definition to the following:

We define suicidal ideation (SI) as thinking about, considering, or planning suicide; desire to die; desire to stop living; or engagement in highly dangerous activities or self harm with the implicit goal of ending life. It may include admissions of having suicidal ideation in the past or the potential for suicidal ideation in the future. Evidence of suicidal ideation does not follow from hating or frustration with one's own life, extreme anguish or psychological distress, or engagement in highly dangerous activities or self harm where there is no implicit goal of ending one's life. However, explicit statements about wanting to die or engage in suicide are taken literally.

### SI Classification Algorithm

A number of methods have been implemented to detect suicidal ideation from user-generated text on social media [1]. However, here we use a simpler algorithm and leave the implementation of these other classifiers as a future project.

We expected SI expression to be fairly rare among /r/Depression posts. Thus, in order to get a good estimate of the drop out risk attributable to SI, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors. However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive author to be so rare, and hence not have much influence on our estimate of the SI-negative drop out risk. In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.

To achieve this goal, we implement an algorithm that searches post text for at least one phrase from a reference list of SI-expressive phrases. We generated our reference list by programatically expanding a sample of SI-expressive phrases which were hand-picked from 750 random June /r/Depression comments. The algorithm is detailed in [Supplement/SI Classification](Supplement.html).

### Estimation of Drop Outs

Our goal is to estimate the number of SI-attributable drop outs. We do this by specifying a parametric Bayesian model and taking Monte-Carlo samples from the posterior. Mathematically, we write SI-attributable drop outs as:
$$E(\sum_i Q_i | SI_i=1) - E(\sum_i Q_i | SI_i=0)$$

Let $i$ index the authors. Let $Q_i$ be the (unobserved) event that author $i$ has quit Reddit. Let $t_i$ be the time since observing the most recent post from author $i$. Let $y_i$ be the (unobserved) length of time from the most recent post to the next post in the future. If author $i$ has quit Reddit, then $y_i = \infty$. Let $n_i$ be the observed number of intervals between posts for author $i$. Let $\bar{\epsilon_i}$ be the observed average time between Reddit posts for author $i$. Let $SI_i$ be the indicator that author $i$ is SI-positive in June. Let $\rho$ be the prior probability (which we define) that any author drops out of Reddit.

First assume that the post histories of each author are a Poisson process, and so observed times between posts are exponentially distributed with parameter $\lambda_i$. For each $\lambda_i$, specify the prior distribution $\lambda_i \sim gamma(1,1)$. 
Hence the posterior for $\lambda_i$ is 
$\lambda_i \big |n_i,\bar{\epsilon_i} \sim gamma(n_i + 1, 1 + n_i\cdot\bar{\epsilon_i})$.

Given $\lambda_i$ and prior $\rho$, we are able to calculate the probability that the author has stopped using Reddit using Bayes Rule.
$$ P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)
            =  \frac{P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) \cdot \rho}
                        {P(y_i > t_i|\lambda_i, t_i, \rho)}
            =   \frac{\rho} {e^{-\lambda_i\cdot t_i} \cdot (1-\rho) + \rho} 
$$ 
Note that $P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) = 1$ since $y_i = \infty$ for the event $Q_i$. Also note that marginal to $Q_i$, $y_i$ follows a mixture of infinity with probability $\rho$ and an exponential with parameter $\lambda_i$ and probability $\rho$.

Now, if we consider each $Q_i$ to be independent, and we are given $P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$ for each author, then 
$$E(\sum_i Q_i| SI_i = 1) - E(\sum_i Q_i| SI_i = 0) = 
      \sum_i (-1)^{SI_i +1} P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$$

Hence, using these formulas, we can generate Monte-Carlo samples from the posterior distribution for the expected number of drop-outs attributable to SI.

# Results

### June /r/Depression

For the month of June, /r/Depression contained 22,041 posts, representing contributions from 7,572 authors. We identified 547 SI-positive posts from 492 unique authors. In a simple random sample of 100 SI-positive posts, and 100 SI-positive posts, we estimated the positive predictive value to be 88% (80%, 94%) and the negative predictive value to be 96% (90%, 99%).

### User Follow-Up

We were able to scrape post histories for 488 of the 492 SI-positive authors from June as well as 474 randomly sampled SI-negative authors from June.

```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=13, fig.height=6}
user.data = 
      author.summary %>%
      group_by(author) %>%
      filter(newest == max(newest)) %>%
      ungroup %>%
      group_by(si.author)%>%
      transmute(author, rank_newest = rank(newest)) %>%
      ungroup %>%
      select(-si.author) %>%
      merge(user.data, by = "author", all.y=T)
user.data$point.label = 
      ifelse(user.data$class, "SI",
      ifelse(user.data$r.depression, "/r/Depression","other")) %>%
      ordered(labels = c("Other Subreddit", "/r/Depression", "SI Expressive"))
user.data$si.group = 
      ifelse(user.data$si.author, "SI-Positive in June /r/Depression",
             "SI-Negative in June /r/Depression")
### Make plot
ggplot(data = subset(user.data, date > jan1)) +
geom_point(aes(y=rank_newest,x=date, 
               color=point.label, alpha=point.label, 
               size=point.label)) + 
ggtitle("Distribution of Post Dates across Authors between Jan. and Oct.") +
ylab("Author Rank by Newest Post") + xlab("Date") +
geom_vline(aes(xintercept = as.numeric(july1)), alpha=0.5) + 
geom_vline(aes(xintercept = as.numeric(june1)), alpha=0.5) + 
scale_colour_manual(name = "Post\nCharacteristics",
                    values = c("grey","darkblue", "red")) + 
scale_size_manual(name = "Post\nCharacteristics",
                  values = c(0.1,0.1,0.3)) + 
scale_alpha_manual(name = "Post\nCharacteristics",
                   values = c(0.1,0.1,1)) + 
theme_bw(20) + 
theme(legend.key = element_blank(),
      legend.position=c(1,0),
      legend.justification = c(1,0),
      legend.background = element_rect(fill=alpha('grey', 0)))+
facet_wrap("si.group") +
guides(color = guide_legend(override.aes = list(size=5, alpha = 1)))

```

**Figure 1: Post histories for SI-Positive authors and SI-Negative authors are different.** Author ids are sorted along the y axis by time of the most recent post. Dates of posts are sorted along the x axis. Each horizontal strip of points represents a user history. Posts are red if they contain SI expression, regardless of their subreddit. Posts without SI expression are blue if they are in the subreddit /r/Depression, or they are otherwise grey. Vertical grey lines outline the month of June, from which data was sampled.

Figure 1 reveals a number of characteristics about the authors in our study. First, we note that those authors who posted more recently tended to post more often, which is expected. Second we see that many authors made multiple SI-positive posts, even among the group that was SI-negative in June /r/Depression.

Figure 1 also illuminates a number of important differences between the SI-positive and SI-negative groups. The figure shows that nearly 170 of our 491 authors had their last post in June, which was the period that we used to sample from. In comparison, only about 100 of the SI-negative authors had their last post in June. Fourth, of these 170 authors, many did not post frequently before dropping-off Reddit.

### Drop-Out Rate Estimates

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=5}
load("Data/Posteriors/Attributable_10e-10.Rdata")
ci = quantile(post.excess, probs = c(0.025, 0.975))
```

The histogram below represents the posterior distribution for the rate of drop outs for authors whose June /r/Depression comments were SI-positive.
Our 95% credible interval is (`r ci`). Hence, there is a 95% probability that the expected SI-attributable drop outs for authors in June 2016 /r/Depression is between `r ci[1]` and `r ci[2]`.

```{r, echo=FALSE, warning=FALSE, message=F,fig.height=4, fig.width=5}
ggplot() +
geom_histogram(aes(x=post.excess),  
               color="black", fill="blue", alpha=0.7) +
ggtitle("Posterior Distribution for\nSI-Attributable Drop-Outs (Prior = 10e-4)")+
xlab("Expected Number of SI-Attributable Drop-Outs") + 
ylab("Count") + 
theme_bw(14)
```

**Figure 2: 10,000 Posterior Monte-Carlo Samples for the Expected Number of SI-Attributable Drop-Outs.**

### Sensitivity to Priors

We found that our conclusions were sensitive to our specified prior probability that any author dropped out. The plot below shows posterior credible intervals for the expected number of SI-attributable drop outs in June /r/Depression.

If we set our prior probability of dropping out equal to 0.5, we would conclude that among the 491 authors who wrote SI-postitive posts in June /r/Depression, there were only about 14 excess reddit drop outs. However, when we set our prior probability of dropping out below $10^{-5}$, our estimates for excess dropouts associated with SI are in the range of 45 to 55.

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=5}
load("Data/Posteriors/Attributable_All.Rdata")
load("Data/Posteriors/Priors_All.Rdata")
library(scales)
ggplot() +
geom_errorbar(aes(ymax = post_p[3,], ymin = post_p[1,], x=prior.p)) +
geom_point(aes(y= post_p[2,], x=prior.p)) + 
scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) + 
theme_bw(14) + 
xlab("Prior Probability of Quitting Reddit") + 
ylab("Expected SI-Attributable Drop-Outs") +
ggtitle("Posterior Credible Intervals for\nTotal SI-Attributable Drop-Outs") 
```

**Figure 3: Posterior credible intervals for SI-attributable drop outs across many priors.** Each point represents a posterior median for SI-attributable drop outs, while bars represent 2.5% and 97.5% quantiles. Prior probabilities of dropping out range from $\rho = 0.5$ to $\rho=10^{-15.5}$

Given the discrepancy in conclusions we would draw between a large prior and small prior, we reccomend that a small prior be used for the following reason: large prior probabilities of dropping out inflate author-specific posterior probabilities of dropping out with artificial evidence. If instead we use a small prior-probability of dropping out, our posterior estimate that a given author has dropped out relies more heavily on their data: whether the time since an author's most recent post is unusually high compared to their post history. Hence, the estimates of total number of drop outs among SI-postitive and SI-negative authors respectively is (1) more conservative and (2) requires more data-based evidence. Consequently, the difference in estimated drop out rates between SI-positive and SI-negative authors is driven more by the data and less by the prior.

In our previous results, we present a credible interval derived from a prior of $10^{-5}$ for this reason. The interpretation of this prior is as follows: without seeing any data, we would expect about 0.01 of our approximate 1,000 authors to drop out of reddit.

# Discussion

Online communities present a unique platform where people can address their own mental health concerns. However, it has become increasingly difficult to ensure that these communities promote mental wellness. Social media lacks the inferential tools to study the mental health of it's online commuities, especially when it comes to suicide prevention.

Most social media platforms do not have data about user suicides, and therefore can not estimate community suicide rates using traditional inferential tools. In this paper, we proposed an alternative parameter, SI-attributable drop outs, that should theoretically be linked to a suicide rate. However, it is extraordinarily important that researchers do not yet interpret this parameter as a suicide rate. Right now, it is only an estimate of the number of users who abandon their account after expressing suicidal ideation. A great deal of validation work would need to first establish a link between suicide rates and SI-attributable drop outs. For example, it would necessary to implement this method in an online community where true suicides could actually be observed.

We list a number of extensions and adjustments for this project in order of priority.

First, our method does not properly account for counfounding relationships between SI and droping out. For example, moderators ban authors for "trolling." If being banned for trolling is more prevalent among SI-negative (or SI-positive) authors, our estimate of the drop outs attributable to SI will be biased downward (or upward).

Second, we need to adjust our estimates to account for the error in our SI classification algorithm. (See [June Depression](#june-/r/depression).) Not knowing whether each author truly expressed SI in their text data should inflate the uncertainty of the estimate.

Third, we need to propose a framework for extending our estimation longitudionally. Community moderators will want to measure SI-attributable drop outs before and after interventions. However, it is not yet clear how we will measure SI-attributable drop outs over time, especially when so many authors repeatedly express SI. In this paper, we only estimate the SI-attributable drop outs for June 2016 authors with data collected at a single time point (October 10, 2016).

Fourth, we need to better assess the fit of our model to the observed data. We use a parametric Bayesian approach to estimate each author's individual probability of having dropped out. In this framework, we assumed that times between an author's posts follow an exponential distribution. However, mixture of exponential distributions with adjustments for temporal trends may better fit the data.

Fifth, we ignore the information the author's text may contain about dropping out or attempting suicide. For example, we do not differentiate between suicidal ideation and suicide plans. A body of psychological literature documents the importance of accounting for and quantifying suicidal intent and planning when examining suicide risk [4]. However, attempting to mine such psychological measures from a large amount of text data is far beyond the scope of this paper and easily beyond the frontiers of psychological science and machine learning.

# References

1. Choudhury, M. D., Kiciman, E., Dredze, M., Coppersmith, G., & Kumar, M. (2016). Discovering Shifts to Suicidal Ideation from Mental Health Content in Social Media. Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems - CHI '16. doi:10.1145/2858036.2858207

2. Crosby, A. E., Ortega, L., & Melanson, C. (2011). Self-directed violence surveillance: Uniform definitions and recommended data elements (CDC).

3. Eggerston, L. (2015, August 11). Social media embraces suicide prevention. Retrieved October 28, 2016, from http://www.cmaj.ca/content/187/11/E333.short

4. Nock, M. K., Borges, G., Bromet, E. J., Cha, C. B., Kessler, R. C., & Lee, S. (2008). Suicide and Suicidal Behavior. Epidemiologic Reviews, 30(1), 133–154. http://doi.org/10.1093/epirev/mxn002

### 2016-10-29 Supplement.Rmd
edited rough draft. added figure descriptions
clean house

@@
 ---
+
+```{r setup, message=FALSE, echo=FALSE}
+library(ggplot2)
+library(dplyr)
+library(chron)
+library(lubridate)
+options(width = 200)
+```
 
@@
 [Scripts/0_Scrape_June_Data.py](Scripts/0_Scrape_June_Data.py).
-Parse the json files for each thread for the main post and comments. For each, grab information on author, title (if applicable), text, creation date, name/link id, etc. 
+We parse the json files for each thread for the main post and comments. For each, grab information on author, title (if applicable), text, creation date, name/link id, etc. 
 (See code: [Scripts/1_Read_Json_Files.R](Scripts/1_Read_Json_Files.R))
@@
 
+```{r, message=FALSE}
+load(file = "Data/June_Depression_Sample/June_Posts_Classified.RData")
+user.data$author[user.data$author == "\\[deleted\\]"] = NA
+user.data$text[grepl("\\[deleted\\]",user.data$text)] = NA
+summarise(user.data,
+          total_posts = n(),
+          total_si = sum(si),
+          total_authors_si = length(unique(author[si])),
+          unique_authors = length(unique(author)),
+          unique_threads = length(unique(thread_id)))
+authors = with(user.data, unique(author[si])) %>% na.omit()
+authors.noSI = with(user.data, unique(author[!si])) %>% na.omit() %>% sample(500)
+length(authors); length(authors.noSI)
+rm(authors, authors.noSI, user.data)
+```
+
 3. **Scrape Author Data.**
@@
 We collected ours at 4pm on October 10, 2016.
-(See code: [Scripts/3.1_Scrape_User_Data.R](Scripts/3.1_Scrape_User_Data.R) and
-[Scripts/3.2_Scrape_NoSI_User_Data.R](Scripts/3.2_Scrape_NoSI_User_Data.R))
+We user this code to scrape the author data: [Scripts/3.1_Scrape_User_Data.R](Scripts/3.1_Scrape_User_Data.R),
+[Scripts/3.2_Scrape_NoSI_User_Data.R](Scripts/3.2_Scrape_NoSI_User_Data.R). 
+It takes nearly 24 hours to run. 
+We use this code to classify the comments as SI-expressive:
+[Scripts/4.1_Classify_SI_Author_Data.R](Scripts/4.1_Classify_SI_Author_Data.R),
+[Scripts/4.2_Classify_NoSI_Author_Data.R](Scripts/4.2_Classify_NoSI_Author_Data.R).
+This takes ~30 minutes to run. 
+We use this code to combine the data and format it for plots, as well as summarize it for the estimation: 
+[Scripts/5_Combine_Authors.R](Scripts/5_Combine_Authors.R).
 
-4. **Drop-Out Estimation.** Estimate the expected number of drop-outs attributable to SI. 
-(See derivation: [Estimation of Drop-Out Totals](#estimation-of-drop-out-totals), 
-see code: [Scripts/6_MC_Estimation.R](Scripts/6_MC_Estimation.R))
+```{r}
+load("Data/SI_Author_Sample/June_Authors_Combined.RData")
+user.data %>%
+      group_by(si.author) %>%
+      summarise(
+          n_author = length(unique(author)),
+          n_posts = n(),
+          posts_per_author = n_posts / n_author,
+          n_posts_si = sum(class, na.rm=T))
+```
 
-5. If a bayesian approach was used, examine the relationship between the estimate and the priors.
-
-# Estimation of Drop-Out Totals
-
-Derivation:
-
-Let $i$ index the authors.
-Let $Q_i$ be the (unobserved) event that author $i$ has quit Reddit.
-Let $t_i$ be the time since observing the most recent post from author $i$.
-Let $y_i$ be the (unobserved) length of time from the most recent post to the next post in the future.
-If author $i$ has quit Reddit, then $y_i = \infty$.
-Let $n_i$ be the observed number of intervals between posts for author $i$.
-Let $\bar{\epsilon_i}$ be the observed average time between Reddit posts for author $i$.
-Let $SI_i$ be the (unobserved) indicator that author $i$ dropped off of Reddit.
-Let $\rho$ be the prior probability (which we define) that any author drops out of Reddit.
-
-Our goal is to do monte-carlo sampling from the posterior distribution of 
-$E(\sum_i Q_i | SI_i=1) - E(\sum_i Q_i | SI_i=0)$.
-
-First assume that the post histories of each author are a Poisson process, and so observed times between posts are exponentially distributed with parameter $\lambda_i$.
-For each $\lambda_i$, specify the prior distribution $\lambda_i \sim gamma(1,1)$.
-Hence the posterior for $\lambda_i$ is 
-$\lambda_i \big |n_i,\bar{\epsilon_i} \sim gamma(n_i + 1, 1 + n_i\cdot\bar{\epsilon_i})$. [CITE RESULT].
-
-Given $\lambda_i$ and prior $\rho$, we are able to calculate the probability that the author has stopped using Reddit using Bayes Rule.
-$$ P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)
-            =  \frac{P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) \cdot \rho}
-                        {P(y_i > t_i|\lambda_i, t_i, \rho)}
-            =   \frac{\rho} {e^{-\lambda_i\cdot t_i} \cdot (1-\rho) + \rho} 
-$$ 
-Note that $P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) = 1$ since $y_i = \infty$ for the event $Q_i$.
-Also note that marginal to $Q_i$, $y_i$ follows a mixture of infinity with probability $\rho$ and an exponential with parameter $\lambda_i$ and probability $\rho$.
-
-Now, if we consider each $Q_i$ to be independent, and we are given $P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$ for each author, then 
-$$E(\sum_i Q_i| SI_i = 1) - E(\sum_i Q_i| SI_i = 0) = 
-      \sum_i (-1)^{SI_i +1} P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$$
-
-Hence, using these formulas, we can generate monte-carlo samples from the posterior distribution for the expected number of drop-outs attributable to SI.
+4. **Drop-Out Estimation.** Estimate the expected number of drop-outs attributable to SI. We save the posterior samples to plot in the paper.
+(See code: [Scripts/6_MC_Estimation.R](Scripts/6_MC_Estimation.R))
 
 # SI Classification
+
+A number of methods have been implemented to detect suicidal ideation from user-generated text on social media [1].
+However, here we use a simpler algorithm and leave the implementation of these other classifiers as a future project.
+
+We expected SI expression to be fairly rare among /r/Depression posts.
+Thus, in order to get a good estimate of the drop out risk attributable to SI, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors.
+However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive author to be so rare, and hence not have much influence on our estimate of the SI-negative drop out risk.
+In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.
+
+To achieve this goal, we implement an algorithm that searches post text for at least one phrase from a reference list of SI-expressive phrases.
+We generated our reference list by programatically expanding a sample of SI-expressive phrases which were hand-picked from 750 random June /r/Depression comments.
+The algorithm is detailed in [Supplement/SI Classification](Supplement.html).
 
@@
 * I [am opposed to] [living]
+
+##### SI Classification: PPV & NPV
+
+We use the script [Scripts/99_Assign_Test_Values.R](Scripts/99_Assign_Test_Values.R) to sample 200 posts and hand-classify them as having true SI or not.
+
+```{r ppv, message = FALSE, warning=FALSE}
+load(file = "Data/Test/Test_Classified.Rdata")
+colnames(test.sample)
+with(test.sample, table(si, suicidal))
+library(Hmisc)
+binconf(c(88, 96), c(100, 100), alpha=0.05, method=c("exact"))
+```
+
+We can see that the positive predictive value is 88% and the negative predictive value is 96%.

### 2016-10-29 Scripts/0_Pretest_SI_Classification/Assign_Pretest_Values.R

@@ -1,18 +1,0 @@
-pretest <- read.csv(file="Scrape_Reddits/pretest.csv", 
-                    header=F, stringsAsFactors=F)
-
-colnames(pretest) <- c("title", "subreddit", "author", "date", "link", "text")
-
-pretest <- cbind(pretest, suicidal=0, suicidal.past=0, mental.disorder=0)
-
-for(i in 1:nrow(pretest)){
-      print(pretest[i,"text"])
-      suicidal <- readline(prompt="Current Suicide Ideation (0,1):") 
-      suicidal.past <- readline(prompt="Past Suicide Ideation (0,1):") 
-      mental.disorder <- readline(prompt="Some Mental Disorder (0,1):") 
-      pretest[i,7:9] <- c(suicidal, suicidal.past, mental.disorder)
-}
-
-write.csv(pretest, file="Scrape_Reddits/classified_pretest.csv")
-
-

### 2016-10-29 Scripts/2_Combine_Classify_June_Posts_Comments.R

@@ -1,5 +1,5 @@
 ### Setup
-      load(file="Data/June_NoSI_Authors_Data.RData")
+      load(file="Data/June_Depression_Sample/June_Posts.RData")
       library(dplyr)
       
 ### Define Functions
@@ -18,7 +18,7 @@
       rm(comm.data, post.data, get.date)
       
 ### Classify Suicide Ideation
-      source("Scripts/2.2_SI_Classification/ideation_phrases.R")
+      source("Scripts/99_ideation_phrases.R")
       
       ### Get phrases
             key.phrases = clean.text(key.phrases)

### 2016-10-29 Scripts/3.1_Scrape_User_Data.R

@@ -1,6 +1,6 @@
 
 ### get functions
-      source(file="Scripts/functions_scrape_reddit_comment.R")
+      source(file="Scripts/3.3_Scrape_Functions.R")
       load(file = "Data/June_Depression_Sample/June_Unique_NoSI_Authors.RData")
       authors.noSI = na.omit(authors.noSI)
       
@@ -21,4 +21,4 @@ for(user in authors.noSI){
 }
 rm(comm.vars, get_reddit_user, post.vars, replace_null, 
    user, user_data_frame, user.comments, user.submitted)
-save.image(file = "Data/June_NoSI_Authors_Data.RData")
+save.image(file = "Data/SI_Author_Sample/June_NoSI_Authors_Data.RData")

### 2016-10-29 Scripts/3.2_Scrape_NoSI_User_Data.R

@@ -1,6 +1,6 @@
 
 ### get functions
-      source(file="Scrape_User_Data/functions_scrape_reddit_comment.R")
+      source(file="Scripts/3.3_Scrape_Functions.R")
       load(file = "Data/June_Unique_SI_Authors.RData")
       authors = na.omit(authors)
       
@@ -21,4 +21,4 @@ for(user in authors){
 }
 rm(comm.vars, get_reddit_user, post.vars, replace_null, 
    user, user_data_frame, user.comments, user.submitted)
-save.image(file = "Data/June_Authors_Data.RData")
+save.image(file = "Data/SI_Author_Sample/June_Authors_Data.RData")

### 2016-10-29 Scripts/4.1_Classify_SI_Author_Data.R

@@ -27,7 +27,7 @@ user.data =
       rbind(user.post.data, user.comment.data)
 
 ### Get phrases
-source("Scripts/SI_Classification/ideation_phrases.R")
+source("Scripts/99_ideation_phrases.R")
       key.phrases = clean.text(key.phrases)
       key.phrases = key.phrases[nchar(key.phrases) > 8]
       key_phrase_regex = paste(key.phrases, collapse="|")

### 2016-10-29 Scripts/4.2_Classify_NoSI_Author_Data.R

@@ -26,7 +26,7 @@ user.data =
             rbind(user.post.data, user.comment.data)
 
 ### Get phrases
-      source("Scripts/SI_Classification/ideation_phrases.R")
+      source("Scripts/99_ideation_phrases.R")
       key.phrases = clean.text(key.phrases)
       key.phrases = key.phrases[nchar(key.phrases) > 8]
       key_phrase_regex = paste(key.phrases, collapse="|")

### 2016-10-29 Scripts/6_MC_Estimation.R

@@ -10,7 +10,7 @@
                       eps.bar = mean(time.last, na.rm=T),
                       t = as.numeric(october10 - max(date)),
                       si.author = si.author[1]) %>%
-            filter(t < 150)
+            filter(t < as.numeric(october10-june1))
       n = author.summary$n
       eps = author.summary$eps.bar
       eps[is.na(eps)] = 0 

### 2016-10-29 Scripts/99_Assign_Test_Values.R

@@ -1,0 +1,27 @@
+load(file="Data/June_Depression_Sample/June_Posts_Classified.RData")
+require(dplyr)
+
+### Sample 100 of each SI-positive and SI-negative
+      si.positive.sample = 
+            filter(user.data, si) %>%
+            sample_n(100)
+      
+      si.negative.sample =
+            filter(user.data, !si) %>%
+            sample_n(100)
+      
+      test.sample = rbind(si.negative.sample, si.positive.sample)
+
+rm(user.data, si.positive.sample, si.negative.sample)
+
+for(i in 1:nrow(test.sample)){
+      cat(test.sample[i,"text"], "\n")
+      test.sample$suicidal[i] <- readline(prompt="Current Suicide Ideation (0,1):") 
+      test.sample$phrase[i] <- readline(prompt="SI evidence:") 
+}
+
+test.sample$suicidal[!test.sample$phrase ==""] <- 1
+test.sample$suicidal[test.sample$suicidal ==""] <- 0
+test.sample$suicidal[!test.sample$suicidal %in% c("0","1")] <- test.sample$phrase[!test.sample$suicidal %in% c("0","1")] 
+
+save(test.sample, file="Data/Test/Test_Classified.Rdata")

### 2016-10-29 Scripts/99_ideation_phrases.R

@@ -1,0 +1,93 @@
+
+library(dplyr)
+
+### Clean text
+clean.text <-function(x){
+      x = gsub(" |\t|\n", "", x)
+      x = gsub("[[:punct:]]", "", x)
+      a = paste(word.list$accessories, collapse="|")
+      x = gsub(a, "", x)
+      return(tolower(x))
+}
+
+### Read in the suicide lexicon
+words <- readLines("Scripts/99_Suicide_Syntax.txt")
+words <- gsub("\t","",words)
+word.list <- list()
+category <- ""
+
+for(i in words){
+      if(grepl("\\[", i)){
+            category <- sub("\\[","",i)
+            category <- sub("\\]:","",category)
+            category <- sub(" ","_",category)
+            word.list[category] <- ""
+      } else word.list[[category]] <- append(word.list[[category]], i)
+}
+
+word.list <- lapply(word.list, function(x) x[-1])
+
+### Generate Suicidal Phrases
+make.phrases <- function(x, i){
+      sub(" \'", "\'", 
+      paste(i, 
+      expand.grid(word.list[x]) %>% 
+      apply(1, paste, collapse=" "))) 
+}
+
+### Direct admission of suicide ideation
+      # [iam] [intentioning verb] [suicide verb]
+      i.am.intentioningverb.suicideverb <- make.phrases(c("iam", "intentioning_verb", "suicide_verb"), i="")
+
+      #[I am] [thinking verb] [suicide noun]
+      i.am.thinkingverb.suicidenoun <- make.phrases(c("iam", "thinking_verb","suicide_noun"), i="")
+      
+      #I [intention verb] [suicide verb]
+      i.intentionverb.suicideverb <- make.phrases(c("intention_verb", "suicide_verb"), i="i")
+      
+      #I [possess] [think noun] [suicide noun]
+      i.possess.thinknoun.suicidenoun <- make.phrases(c("possess", "think_noun", "suicide_noun"), i="i")
+      
+      #I [think verb] [suicide noun]
+      i.thinkverb.suicidenoun <- make.phrases(c("think_verb", "suicide_noun"), i="i")
+      
+      #If I [suicide verb]
+      i.suicideverb <- make.phrases(c("suicide_verb"), i="i")
+      
+      #[iam] [suicide adj]
+      iam.suicideadjective <- make.phrases(c("iam", "suicide_adj"), i="")
+      
+      # me to [suicide verb]
[…]

### 2016-10-29 Scripts/SI_Classification/Assign_Test_Values.R

@@ -1,27 +1,0 @@
-load(file="Data/June_Depression_Sample/June_Posts_Classified.RData")
-require(dplyr)
-
-### Sample 100 of each SI-positive and SI-negative
-      si.positive.sample = 
-            filter(user.data, si) %>%
-            sample_n(100)
-      
-      si.negative.sample =
-            filter(user.data, !si) %>%
-            sample_n(100)
-      
-      test.sample = rbind(si.negative.sample, si.positive.sample)
-
-rm(user.data, si.positive.sample, si.negative.sample)
-
-for(i in 1:nrow(test.sample)){
-      cat(test.sample[i,"text"], "\n")
-      test.sample$suicidal[i] <- readline(prompt="Current Suicide Ideation (0,1):") 
-      test.sample$phrase[i] <- readline(prompt="SI evidence:") 
-}
-
-test.sample$suicidal[!test.sample$phrase ==""] <- 1
-test.sample$suicidal[test.sample$suicidal ==""] <- 0
-test.sample$suicidal[!test.sample$suicidal %in% c("0","1")] <- test.sample$phrase[!test.sample$suicidal %in% c("0","1")] 
-
-save(test.sample, file="Data/Test/Test_Classified.Rdata")

### 2016-10-29 Scripts/SI_Classification/Review_Classifier.R

@@ -1,42 +1,0 @@
-load(file="Data/Training/Training_Lacey_Classified.RData")
-load(file="Data/Training/Training_Lacey2_Classified.RData")
-load(file="Data/Training/Training_Linda_Classified.RData")
-load(file="Data/Training/Training_Linda_Classified2.RData")
-
-### Merge Data
-      df1 <- merge(lacey, linda, 
-                   by=c("author", "created", "title", 
-                        "link", "post.text", "file"),
-                   all=T, suffixes = c(".la", ".li"))
-      
-      df2 <- merge(lacey2, linda2, 
-                   by=c("author", "created", "title", 
-                        "link", "post.text", "file"),
-                   all=T, suffixes = c(".la", ".li"))
-      
-      df <- rbind(df1, df2)
-      rm(df1, df2, lacey, linda, linda2, lacey2)
-      
-### Fix bugs
-      df$suicidal.la[df$suicidal.la == ""] <- "0"
-      df$suicidal.la[is.na(df$suicidal.la)] <- "na"
-      df$suicidal.li[is.na(df$suicidal.li)] <- "na"
-      df$suicidal = df$suicidal.li == "1" | df$suicidal.la == "1" 
-      
-### Review Classifiers
-      source("Suicide_Classification_Algorithms/ideation_phrases.R")
-      load(file="Data/June_Posts.RData")
-      
-      ### Get phrases
-      key.phrases = clean.text(key.phrases)
-      key.phrases = key.phrases[nchar(key.phrases) > 8]
-      key_phrase_regex = paste(key.phrases, collapse="|")
-      
-      ### Classify text
-      comm.data$txt = clean.text(comm.data$body)
-      comm.data$class = grepl(key_phrase_regex, comm.data$txt, ignore.case = T)
-      
-      post.data$txt = clean.text(post.data$body)
-      post.data$class = grepl(key_phrase_regex, post.data$txt, ignore.case = T)
-      with(df, table(suicidal, class))
-      

### 2016-10-29 Scripts/SI_Classification/Split_Test_Training.R

@@ -1,11 +1,0 @@
-load(file="Data/Jun1_Post_Data.RData")
-
-all.ind <- sample(1:nrow(post.data), size = 1000, replace = F)
-lacey2 <- post.data[all.ind[1:300],]
-linda2 <- post.data[all.ind[200:499],]
-test2 <- post.data[all.ind[500:1000],]
-
-save(linda2, file="Data/Training_Linda2.RData")
-save(lacey2, file="Data/Training_Lacey2.RData")
-save(test2, file="Data/Test2.RData")
-

### 2016-10-29 Scripts/SI_Classification/ideation_phrases.R

@@ -1,93 +1,0 @@
-
-library(dplyr)
-
-### Clean text
-clean.text <-function(x){
-      x = gsub(" |\t|\n", "", x)
-      x = gsub("[[:punct:]]", "", x)
-      a = paste(word.list$accessories, collapse="|")
-      x = gsub(a, "", x)
-      return(tolower(x))
-}
-
-### Read in the suicide lexicon
-words <- readLines("Scripts/SI_Classification/Suicide_Syntax.txt")
-words <- gsub("\t","",words)
-word.list <- list()
-category <- ""
-
-for(i in words){
-      if(grepl("\\[", i)){
-            category <- sub("\\[","",i)
-            category <- sub("\\]:","",category)
-            category <- sub(" ","_",category)
-            word.list[category] <- ""
-      } else word.list[[category]] <- append(word.list[[category]], i)
-}
-
-word.list <- lapply(word.list, function(x) x[-1])
-
-### Generate Suicidal Phrases
-make.phrases <- function(x, i){
-      sub(" \'", "\'", 
-      paste(i, 
-      expand.grid(word.list[x]) %>% 
-      apply(1, paste, collapse=" "))) 
-}
-
-### Direct admission of suicide ideation
-      # [iam] [intentioning verb] [suicide verb]
-      i.am.intentioningverb.suicideverb <- make.phrases(c("iam", "intentioning_verb", "suicide_verb"), i="")
-
-      #[I am] [thinking verb] [suicide noun]
-      i.am.thinkingverb.suicidenoun <- make.phrases(c("iam", "thinking_verb","suicide_noun"), i="")
-      
-      #I [intention verb] [suicide verb]
-      i.intentionverb.suicideverb <- make.phrases(c("intention_verb", "suicide_verb"), i="i")
-      
-      #I [possess] [think noun] [suicide noun]
-      i.possess.thinknoun.suicidenoun <- make.phrases(c("possess", "think_noun", "suicide_noun"), i="i")
-      
-      #I [think verb] [suicide noun]
-      i.thinkverb.suicidenoun <- make.phrases(c("think_verb", "suicide_noun"), i="i")
-      
-      #If I [suicide verb]
-      i.suicideverb <- make.phrases(c("suicide_verb"), i="i")
-      
-      #[iam] [suicide adj]
-      iam.suicideadjective <- make.phrases(c("iam", "suicide_adj"), i="")
-      
-      # me to [suicide verb]
[…]

### 2016-10-29 Scripts/Summarize_Author_Data.R

@@ -1,30 +1,0 @@
-
-### Load Data
-      load(file="Data/SI_Author_Sample/June_Authors_Data_Classified.RData")
-      colnames(user.data)
-      library(dplyr)
-      library(ggplot2)
-      
-### Summarize Data Frame
-      get.date = function(day) as.POSIXct(day, origin = "1970-01-01", tz = "GMT")
-      oct10 = get.date("2016-10-10 16:00:00")
-      user.summary = 
-            user.data %>%
-            group_by(author) %>%
-            summarise(n = n()-1,
-                      eps = mean(time.last/60/60/24, na.rm=T),
-                      recent = as.numeric(oct10 - max(date)))
-      
-### Save Data
-      save(user.summary, file = "Data/SI_Author_Sample/Author_Summary.RData")
-      
-      
-      ggplot(user.summary) +
-            geom_histogram(aes(x=recent))
-      ggplot(user.summary) +
-            geom_histogram(aes(x=n))
-      ggplot(user.summary) +
-            geom_histogram(aes(x=eps))
-      
-      
-      #filter(user.summary, recent > 135)

### 2016-10-29 Scripts/functions_scrape_reddit_comment.R

@@ -1,58 +1,0 @@
-
-library(httr)
-library(dplyr)
-
-### takes a list and replaces NULL values with NA values
-      replace_null <- function(a.list){
-            null.values <- unlist(lapply(a.list, is.null))
-            a.list[null.values] <- NA
-            return(a.list)
-      }
-
-### grabs data for a user
-      get_reddit_user <- function(username, type = "submitted", after=NA){
-          root_url = "https://api.reddit.com/user/"
-          url = paste0(root_url, username, "/", type)
-          if(!is.na(after)) url = paste0(url, "?after=", after)
-          agent2 = user_agent("blah")
-          reddit = GET(url, agent2)
-          stop_for_status(reddit)
-          cr = content(reddit)
-          return(cr)
-      }
-
-### grabs comments from user data
-      comm.vars =
-            c("author", "created_utc", "likes", "score", "ups", "downs", 
-              "subreddit_id", "link_id", "id", "name", "parent_id",        
-              "body") 
-      post.vars = 
-            c("author", "title", "created_utc", "name", "id", "subreddit_id",
-              "downs",  "ups", "upvote_ratio", "likes", "score", "num_comments",    
-              "permalink",  "url", "selftext")
-      
-      user_data_frame <- function(user, type="submitted", after = NA, n=0){
-            if(n==1000) return(NULL)
-            if(type == "submitted"){
-                  vars = post.vars
-            } else if(type=="comments"){
-                  vars = comm.vars
-            }
-            data.list = get_reddit_user(user, type, after)$data$children
-            data = 
-                  lapply(data.list, 
-                         function(x) {
-                               x$data[vars] %>%
-                               replace_null() %>%
-                               as.data.frame(stringsAsFactors=F)
-                         }) %>%
-                  do.call(what="rbind")
-            if(is.null(data)) return(NULL)
-            if(nrow(data) == 25){
-                  cat(n, ", ")
-                  next.data = 
-                        user_data_frame(user, type, after =  data$name[25], n = n+25)
-                  data = rbind(data, next.data)
-            }
-            return(data)
-      }

### 2016-10-29 Supplement.Rmd
we did it!!!

@@
 
-A number of methods have been implemented to detect suicidal ideation from user-generated text on social media [1].
-However, here we use a simpler algorithm and leave the implementation of these other classifiers as a future project.
+We implement an algorithm that searches post text for at least one phrase from a reference list of SI-expressive phrases.
+We generated our reference list by programatically expanding a sample of SI-expressive phrases which were hand-picked from 750 random June /r/Depression comments.
 
-We expected SI expression to be fairly rare among /r/Depression posts.
-Thus, in order to get a good estimate of the drop out risk attributable to SI, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors.
-However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive author to be so rare, and hence not have much influence on our estimate of the SI-negative drop out risk.
-In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.
+The sample of SI-expressive comments from the 750 posts is here: 
+[Data/Training/suicidal_phrases.txt](Data/Training/suicidal_phrases.txt)
 
-To achieve this goal, we implement an algorithm that searches post text for at least one phrase from a reference list of SI-expressive phrases.
-We generated our reference list by programatically expanding a sample of SI-expressive phrases which were hand-picked from 750 random June /r/Depression comments.
-The algorithm is detailed in [Supplement/SI Classification](Supplement.html).
+We first organize the phrases into linguistic patterns.
+There seemed to be twelve types of phrases, or phrase "recipes", people used to express suicidal ideation.
+Each "recipe" is made up of ingredients, or smaller phrases/words that can be exchanged to convey the same meaning.
+The recipes are listed below.
+The ingredients are listed in the file [Scripts/99_Suicide_Syntax.txt](Scripts/99_Suicide_Syntax.txt).
 
